---
title: "Indicators_Macro"
output: html_document
date: "2022-11-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}

library(anytime)
library(lubridate)
library(timechange)
library(xts)
library(zoo)
library(Quandl)
library(forecast)
library(tidyverse)
library(ggplot2)
library(rlang)
library(PortfolioAnalytics)
library(PerformanceAnalytics)
library(quantmod)
library(TTR)
library(tidyquant)
library(timetk)
```

```{r}
Quandl.api_key("YE-L2_sxPkntzGfHo3vZ")
EDate <- as.Date(Sys.Date())
SDate <- as.Date(EDate-365*100)
YoY <- as.Date(EDate-365)

EDate
EFDate <- as.Date(Sys.Date())
SFDate <- EFDate - 365*100
SFDate
EFDate
```


#Leading indicators are
* Stock market
* House prices
* Retail Sales
* Interest spread (LT & ST bonds)
* Building Permits
* Consumer expectations
* Average weekly hours (manufacturing)
* Manufacturers new orders.

## Stock market - stockmarket_returns
```{r}
#Stock market (S&P)

stockmarket <- tq_get("^GSPC",
                      from ="1920-01-01",
                      get = "stock.prices")

stockmarket_returns <- stockmarket %>%
  tq_transmute(select = adjusted,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "SP500_returns")

stockmarket_returns <- stockmarket %>%
  tq_transmute(select = adjusted,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "SP500_returns")

stockmarket_returns %>%
  ggplot(aes(x = date, y = SP500_returns)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Monthly returns") +
  ggtitle("Monthly Returns for SP500") +
  scale_x_date(date_breaks = "11 years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 

stockmarket_returns %>%
  ggplot(aes(x = SP500_returns)) +
  geom_histogram(binwidth = 0.015) +
  theme_classic() +
  labs(x = "Monthly returns", y = "Frequency") +
  ggtitle("Monthly Returns for SP500") +
  xlim(-0.15,0.25) +
  scale_x_continuous(labels = scales::percent)

summary(stockmarket_returns$SP500_returns)

stockmarket_returns %>% 
  mutate(month = month(date, label = TRUE)) %>% 
  ggplot(aes(x=month ,y=SP500_returns)) +
  geom_boxplot()

#Related to Stocks

DivYield <- Quandl('MULTPL/SP500_DIV_YIELD_MONTH', start_date=SDate, end_date=EDate, type = "xts")

PE <- Quandl('MULTPL/SP500_PE_RATIO_MONTH', start_date=SDate, end_date=EDate, type = "xts")
PEXts <- Quandl('MULTPL/SP500_PE_RATIO_MONTH', start_date=SDate, end_date=EDate, type = "xts")

SP500Earnings <- Quandl('MULTPL/SP500_EARNINGS_MONTH', start_date=SDate, end_date=EDate, type = "xts")

Div <- Quandl('MULTPL/SP500_DIV_MONTH', start_date=SDate, end_date=EDate, type = "xts")

PayoutRatio <- Div/SP500Earnings

chartSeries(PayoutRatio,
            theme = chartTheme("black"))

SnP <- na.omit(cbind(ROC(PEXts),ROC(SP500Earnings)))

charts.PerformanceSummary(SnP)
```


## House prices - house_values
```{r}

#House prices

house_ind <- Quandl.datatable("ZILLOW/INDICATORS")
#house_reg <- Quandl.datatable("ZILLOW/REGIONS")

house_values_data <- Quandl.datatable("ZILLOW/DATA", indicator_id="ZALL",
                                      region_id="102001")

house_values <- xts(x = house_values_data$value, 
                    order.by= house_values_data$date)

house_sales <- Quandl.datatable("ZILLOW/DATA", indicator_id="SAAW", region_id="102001") #**Not included in analysis**

house_sales %>% 
  ggplot(aes(x=date, y=value)) +
  geom_line()

house_values %>%
  as.data.frame() %>%
  rownames_to_column("date") %>%
  ggplot(aes(x=as.POSIXct(date), y=V1)) +
  geom_line()

```

## Retail sales - retail_sales **PROBLEM ASK ALEX**
```{r}
#Retail Sales

retail_sales <- Quandl("FRED/RSXFS",start_date=SDate, end_date=EDate, type="raw", collapse = "monthly")

retail_sales %>% 
  ggplot(aes(x=Date, y=Value)) +
  geom_line()
```

## Interest spread - spread5.3, spread10.3, spread30.3
```{r}
#Interest spread

threemonths <- Quandl("FRED/DTB3",start_date=SDate, end_date=EDate ,type="xts", collapse = "monthly")
#DTB3YoY <- Quandl("FRED/DTB3",start_date=YoY, end_date=EDate ,type="xts", collapse = "daily")

chartSeries(threemonths)

DGS5 <- Quandl("FRED/DGS5", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
#DGS5YoY <- Quandl("FRED/DGS5", start_date=YoY, end_date=EDate ,type="xts", collapse = "daily")

chartSeries(DGS5)

tenyears <- Quandl("FRED/DGS10",start_date=SDate, end_date=EDate,type="xts", collapse = "monthly")
#DGS10YoY <- Quandl("FRED/DGS10",start_date=YoY, end_date=EDate ,type="xts", collapse = "daily")

chartSeries(tenyears)

DGS30 <- (Quandl("FRED/DGS30", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly"))
#DGS30YoY <- Quandl("FRED/DGS30", start_date=YoY, end_date=EDate ,type="xts", collapse = "daily")

chartSeries(DGS30)

DGS30return <- na.omit(ROC(DGS30))

plot(DGS30return)

Spread5.3 <- DGS5 - threemonths
Spread5.3chg <- na.omit(ROC(Spread5.3))
spread10.3 <- tenyears - threemonths
spread10.3chg <- na.omit(ROC(spread10.3))
spread30.3 <- DGS30 - threemonths
spread30.3chg <- na.omit(ROC(spread30.3))

#Visualisation
chartSeries(Spread5.3)
chartSeries(spread10.3)
chartSeries(spread30.3)


Performance <- na.omit(cbind(Spread5.3, spread10.3, spread30.3))
plot(Performance)

rates <- na.omit(cbind(threemonths, DGS5, tenyears, DGS30))
plot(rates)

charts.PerformanceSummary(Performance) #doesn't work, why?

yield_curve <- Quandl("USTREASURY/HQMYC", start_date=SFDate, end_date=EFDate,type="xts", collapse = "monthly")
chartSeries(yield_curve)

#If doesnt work then we will need to do it on excel
#AAA <- Quandl("FRED/DBAA", start_date=SFDate, end_date=EFDate,type="xts", collapse = "monthly") #check on FRED
#AA <- #BAMLC0A2CAA
#A <- #BAMLC0A3CA
#BBB <- #BAMLC0A4CBBB
#BB <- #BAMLH0A1HYBB
#B <- #BAMLH0A2HYB
#CCCandLower <- #BAMLH0A3HYC
```

## Building permits - PERMIT
```{r}
#Building Permits
PERMIT <- Quandl("FRED/PERMIT", start_date=SDate, end_date=EDate,type="xts", collapse = "monthly")
chartSeries(PERMIT)
```

## Consumer expectations - ConsumerSentiment
```{r}
#Consumer expectations
ConsumerSentiment <- Quandl("UMICH/SOC1", start_date=SDate, end_date=EDate,type="xts", collapse = "monthly")
chartSeries(ConsumerSentiment)
```

## Average weekly hours manufacturing **TO REVIEW**
```{r}
#Average weekly hours (manufacturing)
avgWorkHour <- Quandl("FRED/AWHAEMAN", start_date=SDate, end_date=EDate,type="xts", collapse = "monthly")
chartSeries(avgWorkHour)
```

## Manufacturers new orders - NewOrders
```{r}
#Manufacturers new orders.
NewOrders <- Quandl("FRED/AMTMNO", start_date=SDate, end_date=EDate,type="xts", collapse = "monthly")
chartSeries(NewOrders)
```



#Coincident Indicators
* Industrial production Index
* Real Personal incomes
* Manufacturing and trade sales

## Industrial production index - IPI
```{r}
#Industrial production Index
IPI <- AAA <- Quandl("FRED/INDPRO", start_date=SDate, end_date=EDate,type="xts", collapse = "monthly")
chartSeries(IPI)
```

## Income and Expenditure - RealDisposablePersonalIncome
```{r}
#Income and Expenditure
Personal <- NULL

RealMedianHouseHoldIncome <- Quandl("FRED/MEHOINUSA672N", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
plot(RealMedianHouseHoldIncome)

RealDiposablePersonalIncome <- Quandl("FRED/DSPIC96", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
plot(RealDiposablePersonalIncome)

PersonalConsumptionExpenditures <- Quandl("FRED/PCE", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
plot(PersonalConsumptionExpenditures)
PersonalConsumptionExpendituresGrowth <- na.omit(Return.calculate(PersonalConsumptionExpenditures))

PCEDurableGoods <- Quandl("FRED/PCEDG", start_date=SFDate, end_date=EFDate,type="xts", collapse = "monthly")
plot(PCEDurableGoods)
PCEDurableGoodsGrowth <- na.omit(Return.calculate(PCEDurableGoods))

Personal <- cbind(RealDiposablePersonalIncome,PersonalConsumptionExpenditures,PCEDurableGoods)
plot(Personal)

PersonalSavingRate <- Quandl("FRED/PSAVERT", start_date=SFDate, end_date=EFDate,type="xts", collapse = "monthly")
plot(PersonalSavingRate)
PersonalSavingRateGrowth <- na.omit(Return.calculate(PersonalSavingRate))

RealRetailAndFoodSales <- Quandl("FRED/RRSFS",start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
plot(RealRetailAndFoodSales)
RealRetailAndFoodSalesGrowth <- na.omit(Return.calculate(RealRetailAndFoodSales))

DisposablePersonalIncome <- Quandl("FRED/DSPI",start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
plot(DisposablePersonalIncome)
DisposablePersonalIncomeGrowth <- na.omit(Return.calculate(DisposablePersonalIncome))

PersonalConsumptionExpendituresGrowth<- as.ts(PersonalConsumptionExpendituresGrowth)
PCEDurableGoodsGrowth<- as.ts(PCEDurableGoodsGrowth)
PersonalSavingRateGrowth<- as.ts(PersonalSavingRateGrowth)
RealRetailAndFoodSalesGrowth<- as.ts(RealRetailAndFoodSalesGrowth)
DisposablePersonalIncomeGrowth<- as.ts(DisposablePersonalIncomeGrowth)

ggseasonplot(x=PersonalConsumptionExpendituresGrowth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: Personal Consumption Expenditures Growth")

ggseasonplot(x=PCEDurableGoodsGrowth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: PCE Durable Goods Growth")

ggseasonplot(x=PersonalSavingRateGrowth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: Personal Saving Rate Growth")

ggseasonplot(x=RealRetailAndFoodSalesGrowth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: Real Retail And Food Sales Growth")

ggseasonplot(x=DisposablePersonalIncomeGrowth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: Disposable Personal Income Growth")

```

## Real manufacturing and trade sales - man_trade_sales
```{r}
man_trade_sales <- Quandl("FRED/CMRMTSPL", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly" )

chartSeries(man_trade_sales)
```


#Lagging indicators
* Real GDP growth
* Average duration of unemployment 
* Inventory to sales ratio
* Change in unit labor costs 
* Inflation
* Average prime lending rate 
* Ratio of consumer installment debt to income
* Commercial and industrial loans 
* Outstanding loans
* Dollar index

## Real GDP growth - USGdpRealReturn
```{r}
start_date <- as.Date("1947-01-01")
end_date <- as.Date("2021-10-31")

datesRange <- as.tibble(seq(start_date, end_date, "months"))
datesRangFloored <- datesRange %>% 
  rename(Date = value) %>% 
  mutate(Date = as.Date(Date))

USGdpReal <- Quandl("FRED/GDPC1", start_date=start_date, end_date=end_date, type="raw", collapse = "monthly")
USGdpRealXts <- Quandl("FRED/GDPC1", start_date=start_date, end_date=end_date, type="xts", collapse = "monthly")

USGdpRealFloored <- USGdpReal %>%  
  mutate(Date = floor_date(Date, unit = "month"))

joined <- datesRangFloored %>%
  left_join(USGdpRealFloored, by = "Date")

joinedApprox <- joined %>%
  mutate(Value = na.approx(Value))

joinedApprox %>%
  ggplot(aes(x = Date, y = Value)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "GDP") +
  ggtitle("GDP") +
  scale_x_date(date_breaks = "10 years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 

USGdpRealReturn <- na.omit(Return.calculate(USGdpRealXts))
chartSeries(USGdpRealReturn)
USGdpReal <- as.data.frame(USGdpReal) #**TO BE CONVERTED**

USGdpRealReturn<- as.ts(USGdpRealReturn)
ggseasonplot(x=USGdpRealReturn, year.labels=TRUE, year.labels.left=TRUE) +
  #ylim(-0.025,0.025) +
  ylab("%Change") +
  ggtitle("Seasonal plot: GDP Growth")
```


## Employment - avgDurationUne & UnitLaborCosts **BE CAREFUL WITH MONTHS**
```{r}
start_date <- as.Date("1988-01-01")
end_date <- as.Date("2021-01-01")

datesRange <- as.tibble(seq(start_date, end_date, "months"))
datesRangFloored <- datesRange %>% 
  rename(Date = value) %>% 
  mutate(Date = as.Date(Date))

#Labor Force
Employment <- NULL

UNRATE <- Quandl("FRED/UNRATE", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
NROULT <- Quandl("FRED/NROU", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
NROUST <- Quandl("FRED/NROUST", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")

EMRATIO <- Quandl("FRED/EMRATIO", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
UNEMPLOY <- Quandl("FRED/UNEMPLOY", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")

TotalNonFarm_Employed <- Quandl("FRED/PAYEMS",start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
Manufactoring_Employed <- Quandl("FRED/MANEMP", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")

Initial_Claims <- Quandl("FRED/ICSA", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")

Employment <- cbind(TotalNonFarm_Employed,Manufactoring_Employed)
plot(Employment)
plot(UNRATE)

avgDurationUne <- Quandl('FRED/UEMPMEAN', start_date=SDate, end_date=EDate, type = "xts")
chartSeries(avgDurationUne)

UnitLaborCosts <- Quandl('FRED/PRS30006111', start_date=SDate, end_date=EDate, type = "raw", collapse = "monthly") #**TO CHANGE**

UnitLaborCostsFloored <- UnitLaborCosts %>%  
  mutate(Date = floor_date(Date, unit = "month"))

joined <- datesRangFloored %>%
  left_join(UnitLaborCostsFloored, by = "Date")

joinedApprox <- joined %>%
  mutate(Value = na.approx(Value))

joinedApprox %>%
  ggplot(aes(x = Date, y = Value)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Unit Labor Costs") +
  ggtitle("Unit Labor Costs") +
  scale_x_date(date_breaks = "10 years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 
```

## Inventories to sales ratio - total_inv_to_sales
```{r}
# Inventories to sales ratio

retail_inv_to_sales <- Quandl("FRED/RETAILIRSA", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")

manufacturing_inv_to_sales <- Quandl("FRED/MNFCTRIRSA", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")

total_inv_to_sales <- Quandl("FRED/ISRATIO", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")

chartSeries(retail_inv_to_sales)
chartSeries(manufacturing_inv_to_sales)
chartSeries(total_inv_to_sales)
```

## Inflation - core_CPI
```{r}
core_CPI <- Quandl("FRED/CPILFESL", start_date=SFDate, end_date=EFDate, collapse = "monthly")

CPI <- Quandl("FRED/CPIAUCSL", start_date=SFDate, end_date=EFDate , collapse = "monthly")

#CPI_YOY
CPI$Date  <- as.POSIXct(CPI$Date)

CPI <- CPI %>% group_by(month=month(Date)) %>%
  arrange(Date) %>%
  mutate(yearOverYear=Value/lag(Value,1)-1)

core_CPI$Date  <- as.POSIXct(core_CPI$Date)
CPI_CORE <- core_CPI %>% group_by(month=month(Date)) %>%
  arrange(Date) %>%
  mutate(yearOverYear=Value/lag(Value,1)-1)

cpi_spread <- merge.data.frame(CPI, CPI_CORE, by = "Date")
spread <- cpi_spread$yearOverYear.x - cpi_spread$yearOverYear.y
cpi_spread$spread <- spread

CPI %>% 
  ggplot(aes(x=Date, y= yearOverYear)) +
  geom_line()

CPI_CORE %>% 
  ggplot(aes(x=Date, y= yearOverYear)) +
  geom_line()

cpi_spread %>% 
  ggplot(aes(x=Date, y= spread)) +
  geom_line()

```

## Consumer debt to income - consumer_debt_to_income
```{r}
#consumer debt to income
consumer_debt_to_income <- Quandl("FRED/TDSP", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly") #**TO CHANGE**

chartSeries(consumer_debt_to_income)
```


## Commercial and Industrial Loans - CommercialandIndustrial_Loans_All_CommercialBanks & PrimeLendingRate
```{r}

#TOTCI Commercial and Industrial Loans, All Commercial Banks
CommercialandIndustrial_Loans_All_CommercialBanks <- Quandl("FRED/TOTCI", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
chartSeries(CommercialandIndustrial_Loans_All_CommercialBanks)

CommercialandIndustrial_Loans_All_CommercialBanks <- as.ts(CommercialandIndustrial_Loans_All_CommercialBanks)
CommercialandIndustrial_Loans_All_CommercialBanks_Growth <- na.omit(Return.calculate(CommercialandIndustrial_Loans_All_CommercialBanks))
CommercialandIndustrial_Loans_All_CommercialBanks_Growth <- as.ts(CommercialandIndustrial_Loans_All_CommercialBanks_Growth)

PrimeLendingRate <- Quandl('FRED/DPRIME', start_date=SDate, end_date=EDate, type = "xts")
chartSeries(PrimeLendingRate)

ggseasonplot(x=CommercialandIndustrial_Loans_All_CommercialBanks, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: Commercial and Industrial Loans All Commercial Banks")

ggseasonplot(x=CommercialandIndustrial_Loans_All_CommercialBanks_Growth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: Commercial and Industrial Loans All Commercial Banks Growth")

```

## Oustanding loans - outstanding_loans
```{r}
#outstanding loans
outstanding_loans <- Quandl("FRED/TOTLL", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")

chartSeries(outstanding_loans)
```


## Dollar index
```{r}
#Trade weighted dollar index

dollar_index <- tq_get("DX-Y.NYB",
                       get = "stock.prices",
                       from = "1920-01-01")

dollar_index <- dollar_index %>%
  tq_transmute(select = adjusted,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "Index_returns")

dollar_index %>%
  ggplot(aes(x = date, y = Index_returns)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Monthly returns") +
  ggtitle("Monthly Returns for dollar index") +
  scale_x_date(date_breaks = "11 years", date_labels = "%Y")

                       #**TO BE CONVERTED**
```


# Other Economic Indicators


```{r}
#Debt


#GFDEBTN Federal Debt: Total Public Debt
total_public_debt <- Quandl("FRED/GFDEBTN", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
chartSeries(total_public_debt)

total_public_debt <- as.ts(total_public_debt)
total_public_debt_Growth <- na.omit(Return.calculate(total_public_debt))
total_public_debt_Growth <- as.ts(total_public_debt_Growth)

ggseasonplot(x=total_public_debt, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: total public debt")

ggseasonplot(x=total_public_debt_Growth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: total public debt growth")

```


```{r}

#GFDEGDQ188S Federal Debt: Total Public Debt as Percent of Gross Domestic Product
total_public_debt_to_GDP <- Quandl("FRED/GFDEGDQ188S", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
chartSeries(total_public_debt_to_GDP)

total_public_debt_to_GDP <- as.ts(total_public_debt_to_GDP)
total_public_debt_to_GDP_Growth <- na.omit(Return.calculate(total_public_debt_to_GDP))
total_public_debt_to_GDP_Growth <- as.ts(total_public_debt_to_GDP_Growth)

ggseasonplot(x=total_public_debt_to_GDP, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: total public debt to GDP")

ggseasonplot(x=total_public_debt_to_GDP_Growth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: total public debt to GDP growth")

```


```{r}
#EXCSRESNW Excess Reserves of Depository Institutions
excess_reserves <- Quandl("FRED/EXCSRESNW", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
chartSeries(excess_reserves)

excess_reserves <- as.ts(excess_reserves)
excess_reserves_Growth <- na.omit(Return.calculate(excess_reserves))
excess_reserves_Growth <- as.ts(excess_reserves_Growth)

ggseasonplot(x=excess_reserves, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: excess reserves")

ggseasonplot(x=excess_reserves_Growth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: excess reserves growth")

```




