---
title: "Indicators_Macro"
output: html_document
date: "2022-11-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}

library(xts)
library(zoo)
library(Quandl)
library(forecast)
library(tidyverse)
library(ggplot2)
library(rlang)
library(PortfolioAnalytics)
library(PerformanceAnalytics)
library(quantmod)
library(TTR)
library(tidyquant)
library(timetk)

```

```{r}
Quandl.api_key("YE-L2_sxPkntzGfHo3vZ")
EDate <- as.Date(Sys.Date())
SDate <- as.Date(EDate-365*100)
YoY <- as.Date(EDate-365)

EDate
EFDate <- as.Date(Sys.Date())
SFDate <- EFDate - 365*100
SFDate
EFDate
```


#Leading indicators are
* Stock market
* House prices
* Retail Sales
* Interest spread (LT & ST bonds) **TO FINISH**
* Building Permits
* Consumer expectations
* Average weekly hours (manufacturing)
* Manufacturers new orders.

## Stock market
```{r}
#Stock market (S&P)

stockmarket <- tq_get("^GSPC",
                      from ="1920-01-01",
                      get = "stock.prices")

stockmarket_returns <- stockmarket_2 %>%
  tq_transmute(select = adjusted,         
               mutate_fun = periodReturn,   
               period = "daily",      
               col_rename = "SP500_returns")

plot(y= stockmarket$adjusted, x= stockmarket$date )

stockmarket_returns %>%
  ggplot(aes(x = date, y = SP500_returns)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Daily returns") +
  ggtitle("Daily Returns for SP500") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 

stockmarket_returns %>%
  ggplot(aes(x = SP500_returns)) +
  geom_histogram(binwidth = 0.015) +
  theme_classic() +
  labs(x = "Daily returns") +
  ggtitle("Daily Returns for SP500") +
  scale_x_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) +
  annotate(geom = 'text', x = -0.30, y= 200, label = "Extremely\nnegative\nreturns") +
  annotate(geom = 'text', x = 0.430, y = 200, label = "Extremely\npositive\nreturns")
  
#Related to Stocks

DivYield <- Quandl('MULTPL/SP500_DIV_YIELD_MONTH', start_date=SDate, end_date=EDate, type = "xts")

PE <- Quandl('MULTPL/SP500_PE_RATIO_MONTH', start_date=SDate, end_date=EDate, type = "xts")


SP500Earnings <- Quandl('MULTPL/SP500_EARNINGS_MONTH', start_date=SDate, end_date=EDate, type = "xts")


SnP <- na.omit(cbind(ROC(PE),ROC(SP500Earnings)))
charts.PerformanceSummary(SnP)
```

## House prices
```{r}
#House prices

house_ind <- Quandl.datatable("ZILLOW/INDICATORS")
#house_reg <- Quandl.datatable("ZILLOW/REGIONS")

house_values <- Quandl.datatable("ZILLOW/DATA", indicator_id="ZALL", region_id="102001") 

house_sales <- Quandl.datatable("ZILLOW/DATA", indicator_id="SAAW", region_id="102001")

plot(x=house_values$date, y=house_values$value)
plot(x=house_sales$date, y=house_sales$value)
```

## Retail sales
```{r}
#Retail Sales

retail_sales <- Quandl("FRED/RSXFS",start_date=SDate, end_date=EDate ,type="xts", collapse = "daily")
retail_sales_YoY <- Quandl("FRED/RSXFS",start_date=YoY, end_date=EDate ,type="xts", collapse = "daily")

chartSeries(retail_sales)

```

## Interest spread
```{r}
#Interest spread

threemonths <- Quandl("FRED/DTB3",start_date=SDate, end_date=EDate ,type="xts", collapse = "daily")
DTB3YoY <- Quandl("FRED/DTB3",start_date=YoY, end_date=EDate ,type="xts", collapse = "daily")

DGS5 <- Quandl("FRED/DGS5", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "daily")
DGS5YoY <- Quandl("FRED/DGS5", start_date=YoY, end_date=EDate ,type="xts", collapse = "daily")

tenyears <- Quandl("FRED/DGS10",start_date=SDate, end_date=EDate,type="xts", collapse = "daily")
DGS10YoY <- Quandl("FRED/DGS10",start_date=YoY, end_date=EDate ,type="xts", collapse = "daily")

DGS30 <- (Quandl("FRED/DGS30", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "daily"))
DGS30YoY <- Quandl("FRED/DGS30", start_date=YoY, end_date=EDate ,type="xts", collapse = "daily")
DGS30return <- na.omit(ROC(DGS30))

plot(DGS30return)

Spread5.3 <- DGS5 - threemonths
Spread5.3chg <- na.omit(ROC(Spread5.3))
spread10.3 <- tenyears - threemonths
spread10.3chg <- na.omit(ROC(spread10.3))
spread30.3 <- DGS30 - threemonths
spread30.3chg <- na.omit(ROC(spread30.3))

#Visualisation
chartSeries(Spread5.3)
chartSeries(spread10.3)
chartSeries(spread30.3)

charts.PerformanceSummary() #doesn't work, why?

#If doesnt work then we will need to do it on excel
AAA <- Quandl("FRED/BAMLC0A1CAAA", start_date=SFDate, end_date=EFDate,type="xts", collapse = "monthly") #check on FRED
AA <- #BAMLC0A2CAA
A <- #BAMLC0A3CA
BBB <- #BAMLC0A4CBBB
BB <- #BAMLH0A1HYBB
B <- #BAMLH0A2HYB
CCCandLower <- #BAMLH0A3HYC
```

## Building permits
```{r}
#Building Permits
PERMIT <- Quandl("FRED/PERMIT", start_date=SDate, end_date=EDate,type="xts", collapse = "monthly")
```

## Consumer expectations
```{r}
#Consumer expectations
ConsumerSentiment <- Quandl("UMICH/SOC1", start_date=SDate, end_date=EDate,type="xts", collapse = "monthly")
```

## Average weekly hours manufacturing
```{r}
#Average weekly hours (manufacturing)
avgWorkHour <- Quandl("FRED/AWHAEMAN", start_date=SDate, end_date=EDate,type="xts", collapse = "monthly")
```

## Manufacturers new orders
```{r}
#Manufacturers new orders.
NewOrders <- Quandl("FRED/AMTMNO", start_date=SDate, end_date=EDate,type="xts", collapse = "monthly")
```



#Coincident Indicators
* Industrial production Index
* Real Personal incomes
* Manufacturing and trade sales

## Industrial production index
```{r}
#Industrial production Index
IPI <- AAA <- Quandl("FRED/INDPRO", start_date=SDate, end_date=EDate,type="xts", collapse = "monthly")
chartSeries(IPI)
```

## Income and Expenditure
```{r}
#Income and Expenditure
Personal <- NULL

RealMedianHouseHoldIncome <- Quandl("FRED/MEHOINUSA672N", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")
plot(RealMedianHouseHoldIncome)

RealDiposablePersonalIncome <- Quandl("FRED/DSPIC96", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")
plot(RealDiposablePersonalIncome)

PersonalConsumptionExpenditures <- Quandl("FRED/PCE", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")
plot(PersonalConsumptionExpenditures)
PersonalConsumptionExpendituresGrowth <- na.omit(Return.calculate(PersonalConsumptionExpenditures))

PCEDurableGoods <- Quandl("FRED/PCEDG", start_date=SFDate, end_date=EFDate,type="xts", collapse = "quarterly")
plot(PCEDurableGoods)
PCEDurableGoodsGrowth <- na.omit(Return.calculate(PCEDurableGoods))

Personal <- cbind(RealDiposablePersonalIncome,PersonalConsumptionExpenditures,PCEDurableGoods)
plot(Personal)

PersonalSavingRate <- Quandl("FRED/PSAVERT", start_date=SFDate, end_date=EFDate,type="xts", collapse = "quarterly")
plot(PersonalSavingRate)
PersonalSavingRateGrowth <- na.omit(Return.calculate(PersonalSavingRate))

RealRetailAndFoodSales <- Quandl("FRED/RRSFS",start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")
plot(RealRetailAndFoodSales)
RealRetailAndFoodSalesGrowth <- na.omit(Return.calculate(RealRetailAndFoodSales))

DisposablePersonalIncome <- Quandl("FRED/DSPI",start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")
plot(DisposablePersonalIncome)
DisposablePersonalIncomeGrowth <- na.omit(Return.calculate(DisposablePersonalIncome))

PersonalConsumptionExpendituresGrowth<- as.ts(PersonalConsumptionExpendituresGrowth)
PCEDurableGoodsGrowth<- as.ts(PCEDurableGoodsGrowth)
PersonalSavingRateGrowth<- as.ts(PersonalSavingRateGrowth)
RealRetailAndFoodSalesGrowth<- as.ts(RealRetailAndFoodSalesGrowth)
DisposablePersonalIncomeGrowth<- as.ts(DisposablePersonalIncomeGrowth)

ggseasonplot(x=PersonalConsumptionExpendituresGrowth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: Personal Consumption Expenditures Growth")

ggseasonplot(x=PCEDurableGoodsGrowth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: PCE Durable Goods Growth")

ggseasonplot(x=PersonalSavingRateGrowth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: Personal Saving Rate Growth")

ggseasonplot(x=RealRetailAndFoodSalesGrowth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: Real Retail And Food Sales Growth")

ggseasonplot(x=DisposablePersonalIncomeGrowth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: Disposable Personal Income Growth")

```

## Real manufacturing and trade sales
```{r}
man_trade_sales <- Quandl("FRED/CMRMTSPL", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly" )

chartSeries(man_trade_sales)
```


#Lagging indicators
* Real GDP growth
* Average duration of unemployment 
* Inventory to sales ratio
* Change in unit labor costs **TO DO**
* Inflation **TO DO**
* Average prime lending rate **TO DO**
* Ratio of consumer installment debt to income **TO DO**
* Commercial and industrial loans 
* Outstanding loans **TO DO**
* Dollar index

## Real GDP growth
```{r}

USGdpReal <- Quandl("FRED/GDPC1", start_date=SFDate, end_date=EFDate,type="xts", collapse = "quarterly")
chartSeries(USGdpReal)
USGdpRealReturn <- na.omit(Return.calculate(USGdpReal))
chartSeries(USGdpRealReturn)
USGdpReal <- as.data.frame(USGdpReal)

USGdpRealReturn<- as.ts(USGdpRealReturn)
ggseasonplot(x=USGdpRealReturn, year.labels=TRUE, year.labels.left=TRUE) +
  #ylim(-0.025,0.025) +
  ylab("%Change") +
  ggtitle("Seasonal plot: GDP Growth")

```


## Employment
```{r}
#Labor Force
Employment <- NULL

UNRATE <- Quandl("FRED/UNRATE", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")
NROULT <- Quandl("FRED/NROU", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")
NROUST <- Quandl("FRED/NROUST", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")

EMRATIO <- Quandl("FRED/EMRATIO", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")
UNEMPLOY <- Quandl("FRED/UNEMPLOY", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")

TotalNonFarm_Employed <- Quandl("FRED/PAYEMS",start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")
Manufactoring_Employed <- Quandl("FRED/MANEMP", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")

Initial_Claims <- Quandl("FRED/ICSA", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")

Employment <- cbind(TotalNonFarm_Employed,Manufactoring_Employed)
plot(Employment)
plot(UNRATE)

avgDurationUne <- Quandl('FRED/UEMPMEAN', start_date=SDate, end_date=EDate, type = "xts")

UnitLaborCosts <- Quandl('FRED/PRS30006111', start_date=SDate, end_date=EDate, type = "xts")
```

## Inventories to sales ratio
```{r}
# Inventories to sales ratio

retail_inv_to_sales <- Quandl("FRED/RETAILIRSA", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")

manufacturing_inv_to_sales <- Quandl("FRED/MNFCTRIRSA", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")

total_inv_to_sales <- Quandl("FRED/ISRATIO", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")

chartSeries(retail_inv_to_sales)
chartSeries(manufacturing_inv_to_sales)
chartSeries(total_inv_to_sales)
```

## Inflation 
```{r}
core_CPI <- Quandl("FRED/CPILFESL", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")

CPI <- Quandl("FRED/CPIAUCSL", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "quarterly")

CPI_YOY <- Quandl("FRED/CPIAUCSL", start_date=YoY, end_date=EDate ,type="xts", collapse = "daily")

chartSeries(core_CPI)
chartSeries(CPI)
chartSeries(CPI_YOY)

```


## Commercial and Industrial Loans
```{r}

#TOTCI Commercial and Industrial Loans, All Commercial Banks
CommercialandIndustrial_Loans_All_CommercialBanks <- Quandl("FRED/TOTCI", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
chartSeries(CommercialandIndustrial_Loans_All_CommercialBanks)

CommercialandIndustrial_Loans_All_CommercialBanks <- as.ts(CommercialandIndustrial_Loans_All_CommercialBanks)
CommercialandIndustrial_Loans_All_CommercialBanks_Growth <- na.omit(Return.calculate(CommercialandIndustrial_Loans_All_CommercialBanks))
CommercialandIndustrial_Loans_All_CommercialBanks_Growth <- as.ts(CommercialandIndustrial_Loans_All_CommercialBanks_Growth)

PrimeLendingRate <- Quandl('FRED/DPRIME', start_date=SDate, end_date=EDate, type = "xts")

ggseasonplot(x=CommercialandIndustrial_Loans_All_CommercialBanks, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: Commercial and Industrial Loans All Commercial Banks")

ggseasonplot(x=CommercialandIndustrial_Loans_All_CommercialBanks_Growth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: Commercial and Industrial Loans All Commercial Banks Growth")

```

## Dollar index
```{r}
#Trade weighted dollar index

dollar_index <- Quandl("FRED/DTWEXM", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "daily")
chartSeries(dollar_index)
```


# Other Economic Indicators


```{r}
#Debt


#GFDEBTN Federal Debt: Total Public Debt
total_public_debt <- Quandl("FRED/GFDEBTN", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
chartSeries(total_public_debt)

total_public_debt <- as.ts(total_public_debt)
total_public_debt_Growth <- na.omit(Return.calculate(total_public_debt))
total_public_debt_Growth <- as.ts(total_public_debt_Growth)

ggseasonplot(x=total_public_debt, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: total public debt")

ggseasonplot(x=total_public_debt_Growth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: total public debt growth")

```


```{r}

#GFDEGDQ188S Federal Debt: Total Public Debt as Percent of Gross Domestic Product
total_public_debt_to_GDP <- Quandl("FRED/GFDEGDQ188S", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
chartSeries(total_public_debt_to_GDP)

total_public_debt_to_GDP <- as.ts(total_public_debt_to_GDP)
total_public_debt_to_GDP_Growth <- na.omit(Return.calculate(total_public_debt_to_GDP))
total_public_debt_to_GDP_Growth <- as.ts(total_public_debt_to_GDP_Growth)

ggseasonplot(x=total_public_debt_to_GDP, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: total public debt to GDP")

ggseasonplot(x=total_public_debt_to_GDP_Growth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: total public debt to GDP growth")

```


```{r}
#EXCSRESNW Excess Reserves of Depository Institutions
excess_reserves <- Quandl("FRED/EXCSRESNW", start_date=SFDate, end_date=EFDate ,type="xts", collapse = "monthly")
chartSeries(excess_reserves)

excess_reserves <- as.ts(excess_reserves)
excess_reserves_Growth <- na.omit(Return.calculate(excess_reserves))
excess_reserves_Growth <- as.ts(excess_reserves_Growth)

ggseasonplot(x=excess_reserves, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: excess reserves")

ggseasonplot(x=excess_reserves_Growth, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("%Change") +
  ggtitle("Seasonal plot: excess reserves growth")

```





