---
title: "BCI"
output:
  pdf_document: default
  html_document: default
date: "2023-01-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("tidyverse")
library("ggplot2")
library("forecast")
library("Quandl")
library("quantmod")
library("magrittr")
library("tidyquant")
```

```{r}
SDate <- "1975-01-01"
EDate <- Sys.Date()

Quandl.api_key("4nDDuxoarbX1eR9z7KY-")
```


```{r}
Recession <- Quandl('FRED/JHDUSRGDPBR', start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  tq_transmute(select = Value, mutate_fun = to.monthly, indexAt = "firstof")
```

#Firstpart is just for extracting variables or economic indicators that makes up the BCI according to NBER
```{r}
realpersonalincomelesstransfers <- Quandl('FRED/W875RX1', start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  tq_transmute(select = Value, mutate_fun = to.monthly, indexAt = "firstof") %>%
  tq_transmute(select = Value,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "realpersonalincomelesstransfers_returns")

realpersonalincomelesstransfers %>% 
  ggplot(aes(Date, realpersonalincomelesstransfers_returns)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "N° of building permits") +
  ggtitle('Real Personal Income Less Transfers')

#Fourier
realpersonalincomelesstransfers$fourier <- fft(realpersonalincomelesstransfers$realpersonalincomelesstransfers_returns)

# Extract the real and imaginary components of the transform
realpersonalincomelesstransfers$real <- Re(realpersonalincomelesstransfers$fourier)
realpersonalincomelesstransfers$imag <- Im(realpersonalincomelesstransfers$fourier)

realpersonalincomelesstransfers %>% 
  ggplot(aes(Date, real)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year")+
  ggtitle('Real Personal Income Less Transfers')

realpersonalincomelesstransfers %>% 
  ggplot(aes(Date, imag)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") +
  ggtitle('Real Personal Income Less Transfers')
```


```{r}
nonfarmpayrollemployment <- Quandl('FRED/PAYEMS', start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  tq_transmute(select = Value, mutate_fun = to.monthly, indexAt = "firstof")  %>%
  tq_transmute(select = Value,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "nonfarmpayrollemployment")

nonfarmpayrollemployment %>% 
  ggplot(aes(Date, nonfarmpayrollemployment)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "N° of building permits") +
  ggtitle('Non-Farm Payroll')

#Fourier
nonfarmpayrollemployment$fourier <- fft(nonfarmpayrollemployment$nonfarmpayrollemployment)

# Extract the real and imaginary components of the transform
nonfarmpayrollemployment$real <- Re(nonfarmpayrollemployment$fourier)
nonfarmpayrollemployment$imag <- Im(nonfarmpayrollemployment$fourier)

nonfarmpayrollemployment %>% 
  ggplot(aes(Date, real)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year")+
  ggtitle('Real Personal Income Less Transfers')

nonfarmpayrollemployment %>% 
  ggplot(aes(Date, imag)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") +
  ggtitle('Real Personal Income Less Transfers')
```

```{r}
realpersonalconsumptionexpenditures <- Quandl('FRED/DPCERA3M086SBEA', start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  tq_transmute(select = Value, mutate_fun = to.monthly, indexAt = "firstof")  %>%
  tq_transmute(select = Value,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "realpersonalconsumptionexpenditures")

realpersonalconsumptionexpenditures %>% 
  ggplot(aes(Date, realpersonalconsumptionexpenditures)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "N° of building permits") +
  ggtitle('Real personal Consumption Expenditure')

#Fourier
realpersonalconsumptionexpenditures$fourier <- fft(realpersonalconsumptionexpenditures$realpersonalconsumptionexpenditures)

# Extract the real and imaginary components of the transform
realpersonalconsumptionexpenditures$real <- Re(realpersonalconsumptionexpenditures$fourier)
realpersonalconsumptionexpenditures$imag <- Im(realpersonalconsumptionexpenditures$fourier)

realpersonalconsumptionexpenditures %>% 
  ggplot(aes(Date, real)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year")+
  ggtitle('Real Personal Income Less Transfers')

realpersonalconsumptionexpenditures %>% 
  ggplot(aes(Date, imag)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") +
  ggtitle('Real Personal Income Less Transfers')
```
```{r}
ProducerPriceIndex <- Quandl('FRED/PPIACO', start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  tq_transmute(select = Value, mutate_fun = to.monthly, indexAt = "firstof") %>%
  tq_transmute(select = Value,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "ProducerPriceIndex")

ProducerPriceIndex %>% 
  ggplot(aes(Date, ProducerPriceIndex)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "N° of building permits") +
  ggtitle('Producer Price Index')

#Fourier
ProducerPriceIndex$fourier <- fft(ProducerPriceIndex$ProducerPriceIndex)

# Extract the real and imaginary components of the transform
ProducerPriceIndex$real <- Re(ProducerPriceIndex$fourier)
ProducerPriceIndex$imag <- Im(ProducerPriceIndex$fourier)

ProducerPriceIndex %>% 
  ggplot(aes(Date, real)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year")+
  ggtitle('Real Personal Income Less Transfers')

ProducerPriceIndex %>% 
  ggplot(aes(Date, imag)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") +
  ggtitle('Real Personal Income Less Transfers')
```

```{r}
IPI  <- Quandl("FRED/INDPRO", start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  tq_transmute(select = Value, mutate_fun = to.monthly, indexAt = "firstof") %>%
  tq_transmute(select = Value,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "IPI")

IPI %>% 
  ggplot(aes(Date, IPI)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "N° of building permits") +
  ggtitle('Industrial Production Index')

#Fourier
IPI$fourier <- fft(IPI$IPI)

# Extract the real and imaginary components of the transform
IPI$real <- Re(IPI$fourier)
IPI$imag <- Im(IPI$fourier)

IPI %>% 
  ggplot(aes(Date, real)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year")+
  ggtitle('Real Personal Income Less Transfers')

IPI %>% 
  ggplot(aes(Date, imag)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") +
  ggtitle('Real Personal Income Less Transfers')
```
```{r}
unemployment <- Quandl('FRED/UNRATE', start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  tq_transmute(select = Value, mutate_fun = to.monthly, indexAt = "firstof")  %>%
  tq_transmute(select = Value,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "unemployment")


unemployment %>% 
  ggplot(aes(Date, unemployment)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "N° of building permits") +
  ggtitle('Employment Rate')+
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = 0.75, ymax = 1, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = 0.75, ymax = 1, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = 0.75, ymax = 1, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = 0.75, ymax = 1, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = 0.75, ymax = 1, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = 0.75, ymax = 1, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = 0.75, ymax = 1, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1969/12/01"), xmax = as.Date("1970/11/01"), ymin = 0.75, ymax = 1, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1960/04/01"), xmax = as.Date("1961/02/01"), ymin = 0.75, ymax = 1, alpha = .2, fill = 'purple')

#Fourier
unemployment$fourier <- fft(unemployment$unemployment)

# Extract the real and imaginary components of the transform
unemployment$real <- Re(unemployment$fourier)
unemployment$imag <- Im(unemployment$fourier)

unemployment %>% 
  ggplot(aes(Date, real)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year")+
  ggtitle('Real Personal Income Less Transfers')

unemployment %>% 
  ggplot(aes(Date, imag)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") +
  ggtitle('Real Personal Income Less Transfers')
```

```{r}
data <- realpersonalincomelesstransfers %>% left_join(nonfarmpayrollemployment, by = 'Date') %>% left_join(realpersonalconsumptionexpenditures, by = 'Date') %>% left_join(ProducerPriceIndex, by = 'Date') %>% left_join(IPI, by = 'Date') %>% left_join(unemployment, by = 'Date') %>% na.omit()
```


```{r}
data <- realpersonalincomelesstransfers %>% left_join(nonfarmpayrollemployment, by = 'Date') %>% left_join(realpersonalconsumptionexpenditures, by = 'Date') %>% left_join(ProducerPriceIndex, by = 'Date') %>% left_join(IPI, by = 'Date') %>% left_join(unemployment, by = 'Date') %>% na.omit()

data$Date <- as.Date(data$Date, format = "%Y-%m-%d")

#data <- ts(data, start = c(1975, 1), end = c(2021,1),frequency = 12)
```


#This part is for decommposing the timeseries to remove seasonality.
```{r}
# Load the stats package
library("stats")
library(zoo)
```


#This part is for creating the BCI by using principal component analysis.
```{r}
data1 <- data %>% select(-Date)
#pca_data_leading_standardized <- scale(data1)
# Install the tidyverse and principal packages
#install.packages("tidyverse")
#
#install.packages("principal")

# Load the tidyverse and principal packages
library(tidyverse)
#library(principal)
# Apply PCA to the economic indicators data
#pca_results <- prcomp(data1)
# Extract the first principal component
#business_cycle <- pca_results$scores[,1]
# Load the ggplot2 package
library(ggplot2)
#data$business_cycle <- pca_results$scores[,1]
# Create a line plot of the business cycle
#ggplot(data, aes(x = Date, y = business_cycle)) +
 # geom_line()
```

```{r}
library("psych")
news <- cbind(data1$real.x,data1$real.y,data1$real.x.x,data1$real.y.y,data1$real.x.x.x,data1$real.y.y.y)
KMO(news)
pca_data_leading_standardized <- scale(news)
pca_result_leading <- princomp(pca_data_leading_standardized)
pca_result_leading$scores
pca_result_leading$sdev
pca_summary_leading  <- summary(pca_result_leading)
pca_variances_leading  <- var(pca_result_leading$scores)
pca_cumulative_variances_leading  <- cumsum(pca_variances_leading)
pca_var_leading  <- pca_result_leading$sdev^2 / sum(pca_result_leading$sdev^2)
barplot(pca_var_leading, xlab="Principal Component", ylab="Proportion of Variance Explained")
screeplot(pca_result_leading, type="line", main="Scree Plot")
plot(pca_result_leading$scores[,1:2], col=1:nrow(pca_result_leading$scores), xlab="PC1", ylab="PC2")
pca_scores_leading <- as.data.frame(pca_result_leading$scores) %>% 
  select(Comp.1)
values_leading <- realpersonalincomelesstransfers %>% 
  left_join(nonfarmpayrollemployment, by = "Date") %>% 
  left_join(realpersonalconsumptionexpenditures, by = "Date") %>%
  left_join(ProducerPriceIndex, by = "Date") %>%
  left_join(IPI, by = "Date") %>%
  na.omit()
values_leading$index <- pca_scores_leading[,1]
plot(values_leading$Date, values_leading$index)
values_leading %>% 
  ggplot(aes(Date, index)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "Leading index") +
  ggtitle('Leading index for business cycle') +
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')
#+annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')
```
#In the chart above, the BCI was created through the principal component method.

#In the chunks belowe, I will try to create the BCI by using fourier analysis
```{r}
library("stats")
# Compute the discrete Fourier transform of the time series
values_leading$fourier <- fft(values_leading$index)

# Extract the real and imaginary components of the transform
values_leading$real <- Re(values_leading$fourier)
values_leading$imag <- Im(values_leading$fourier)

values_leading$sum <- values_leading$real + 0.2*values_leading$imag
plot(values_leading$real)

# Compute the inverse Fourier transform
#n <- length(values_leading)
#values_leading$inverse_transform <- rep(0, n)
#for (k in 1:n) {
#  values_leading$inverse_transform[k] <- sum(real * cos(2 * pi * (k-1) * (0:(n-1))/n) + imag * sin(2 * pi * (k-1) * (0:(n-1))/n))
#}

# Extract the dates from the data
#dates <- values_leading$Date

# Plot the time series with the dates on the y-axis
plot(values_leading$sum, type = "l", col = "blue", xaxt = "n")
#axis(1, at = 1:n, labels = dates, las = 2)


# Plot the real and imaginary components of the Fourier transform
plot(values_leading$real, type = "l", col = "blue")
plot(values_leading$imag, type = "l", col = "red")

#Recession (Dummy Variable)

values_leading <- values_leading %>% left_join(Recession, by = 'Date') %>% na.omit()

ggplot(values_leading, aes(x=Date, y=real)) +
  geom_line() + geom_point(aes(color = values_leading$Value.y.y.y))+
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')
  
  
 
```



```{r}
DFF <- tq_get("DFF",get = "economic.data" ,from=SDate, collapse = "monthly") %>%  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof")%>%  rename(FFR = price) %>% 
  rename(Date = date)
DFF$increase <- DFF$FFR - lag(DFF$FFR)

# Five-y Bonds
fiveyears_IR <-  tq_get("DGS5",
                         from = SDate,
                         "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(FiveyearsIR = price) %>% 
  rename(Date = date)

# T-Bills
threemonths_IR <- tq_get("DTB3",
                         from = SDate,
                         "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(ThreemonthsIR = price) %>% 
  rename(Date = date)

# 30y - 3m spread
IR_Spread <- fiveyears_IR %>%
    left_join(threemonths_IR, by='Date') %>% 
  mutate(IRSpread = FiveyearsIR - ThreemonthsIR) #%>% 
  #select[-ThirtyyearsIR, -ThreemonthsIR]


```



```{r}

new <-   IR_Spread %>%  left_join(DFF, by='Date') %>% select(-c(FiveyearsIR,ThreemonthsIR,FFR)) %>% na.omit()
data$Date <- as.Date(data$Date, format = "%Y-%m-%d")

#left_join(consumer_sentiment, by='Date') %>%left_join(future_new_orders, by='Date') %>%

```


```{r}
# Load the stats package
library(stats)

new$IRSpread<- ts(new$IRSpread,start = c(1975, 2), end = c(2022,12), frequency = 12)
# Decompose the data using the STL method
decomp_results <- stl(new$IRSpread, s.window = "periodic")

# Extract the residuals (de-seasonalized data)
residuals1 <- decomp_results$time.series[,3]
new$IRSpread <-residuals1

new$increase <- ts(new$increase,start = c(1975, 2), end = c(2022,12), frequency = 12)
# Decompose the data using the STL method
decomp_results <- stl(new$increase, s.window = "periodic")

# Extract the residuals (de-seasonalized data)
residuals2 <- decomp_results$time.series[,3]
new$increase <- residuals2
```

```{r}
new1 <- new %>% select(-Date)
KMO(new1)
pca_data_leading_standardized <- scale(new1)
pca_result_leading <- princomp(pca_data_leading_standardized)
pca_result_leading$scores
pca_result_leading$sdev
pca_summary_leading  <- summary(pca_result_leading)
pca_variances_leading  <- var(pca_result_leading$scores)
pca_cumulative_variances_leading  <- cumsum(pca_variances_leading)
pca_var_leading  <- pca_result_leading$sdev^2 / sum(pca_result_leading$sdev^2)
barplot(pca_var_leading, xlab="Principal Component", ylab="Proportion of Variance Explained")
screeplot(pca_result_leading, type="line", main="Scree Plot")
plot(pca_result_leading$scores[,1:2], col=1:nrow(pca_result_leading$scores), xlab="PC1", ylab="PC2")
pca_scores_leading <- as.data.frame(pca_result_leading$scores) %>% 
  select(Comp.1)
values_leading <- IR_Spread %>%  left_join(DFF, by='Date') %>% select(-c(FiveyearsIR,ThreemonthsIR,FFR)) %>% na.omit()
values_leading$index <- pca_scores_leading[,1]
plot(values_leading$Date, values_leading$index)
values_leading %>% 
  ggplot(aes(Date, index)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "Leading index") +
  ggtitle('Leading index for business cycle') +
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')
#+annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')
```


```{r}
library(stats)
# Compute the discrete Fourier transform of the time series
values_leading$fourier <- fft(values_leading$index)

# Extract the real and imaginary components of the transform
values_leading$real <- Re(values_leading$fourier)
values_leading$imag <- Im(values_leading$fourier)

plot(values_leading$real)

# Compute the inverse Fourier transform
#n <- length(values_leading)
#values_leading$inverse_transform <- rep(0, n)
#for (k in 1:n) {
#  values_leading$inverse_transform[k] <- sum(real * cos(2 * pi * (k-1) * (0:(n-1))/n) + imag * sin(2 * pi * (k-1) * (0:(n-1))/n))
#}

# Extract the dates from the data
#dates <- values_leading$Date

# Plot the time series with the dates on the y-axis
#plot(inverse_transform, type = "l", col = "blue", xaxt = "n")
#axis(1, at = 1:n, labels = dates, las = 2)


# Plot the real and imaginary components of the Fourier transform
plot(values_leading$real, type = "l", col = "blue")
plot(values_leading$imag, type = "l", col = "red")

#Recession (Dummy Variable)
Recession <- Quandl('FRED/JHDUSRGDPBR', start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  tq_transmute(select = Value, mutate_fun = to.monthly, indexAt = "firstof")
values_leading <- values_leading %>% left_join(Recession, by = 'Date') %>% na.omit()

ggplot(values_leading, aes(x=Date, y=real)) +
  geom_line() + geom_point(aes(color = values_leading$Value))+
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')
  
```


#Extracting envronments by clustering the timeseries.
```{r}
#Install the stats and dplyr packages
#install.packages("stats")
#install.packages("dplyr")

# Load the stats and dplyr packages
library(stats)
library(dplyr)


# Calculate the distance between each pair of time series
distance_matrix <- dist(new)

# Run the k-means clustering algorithm
clusters <- kmeans(distance_matrix, centers = 4, iter.max = 10)

# Assign each time series to a cluster
new <- new %>%
  mutate(cluster = clusters$cluster)

ggplot(new, aes(x=Date, y=index)) +
  geom_line()+
  geom_point(aes(color = clusters$cluster))  +
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')

ggplot(new, aes(x=Date, y=IRSpread)) +
  geom_line()+
  geom_point(aes(color = clusters$cluster))  +
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')

ggplot(new, aes(x=Date, y=SP500_returns)) +
  geom_line()+
  geom_point(aes(color = clusters$cluster))  +
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = -0.5, ymax = 0.5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = -0.5, ymax = 0.5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = -0.5, ymax = 0.5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = -0.5, ymax = 0.5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = -0.5, ymax = 0.5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = -0.5, ymax = 0.5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = -0.5, ymax = 0.5, alpha = .2, fill = 'purple')

ggplot(new, aes(x=Date, y=increase)) +
  geom_line()+
  geom_point(aes(color = clusters$cluster))  +
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = -3.5, ymax = 5, alpha = .2, fill = 'purple')
```

