---
title: "Data fetching"
output: html_document
date: "2022-12-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(anytime)
library(lubridate)
library(timechange)
library(xts)
library(zoo)
library(Quandl)
library(forecast)
library(tidyverse)
library(ggplot2)
library(rlang)
library(PortfolioAnalytics)
library(PerformanceAnalytics)
library(quantmod)
library(TTR)
library(tidyquant)
library(timetk)

```

```{r}
Quandl.api_key("YE-L2_sxPkntzGfHo3vZ")
EDate <- as.Date(Sys.Date())
SDate <- as.Date(EDate-365*100)
YoY <- as.Date(EDate-365)

EDate
EFDate <- as.Date(Sys.Date())
SFDate <- EFDate - 365*100
SFDate
EFDate
```

#Leading indicators are
* Stock market
* House prices
* Retail Sales
* Interest spread (LT & ST bonds)
* Building Permits
* Consumer expectations
* Average weekly hours (manufacturing)
* Manufacturers new orders.

## Stock market
```{r}
# S&P500 Prices
stockmarket <- tq_get("^GSPC",
                      from ="1920-01-01",
                      get = "stock.prices")

# S&P500 Returns
stockmarket_returns <- stockmarket %>%
  tq_transmute(select = adjusted,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "SP500Returns") %>% 
  rename(Date = date) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

# S&P500 Dividends
SP500_Div <- Quandl('MULTPL/SP500_DIV_MONTH', 
              start_date=SDate, 
              end_date=EDate)

# S&P500 Dividend Yield
SP500_Div_Yield <- Quandl('MULTPL/SP500_DIV_YIELD_MONTH', 
                   start_date=SDate, 
                   end_date=EDate)

# S&P500 PE Ratios
SP500_PE <- Quandl('MULTPL/SP500_PE_RATIO_MONTH', 
             start_date=SDate, 
             end_date=EDate)

# S&P500 Earnings
SP500_Earnings <- Quandl('MULTPL/SP500_EARNINGS_MONTH', 
                        start_date=SDate, 
                        end_date=EDate)

#PayoutRatio <- Div$Value/SP500Earnings$Value ##


```

## House prices
```{r}

# Zillow home values index
house_values <- Quandl.datatable("ZILLOW/DATA", indicator_id="ZALL", region_id="102001") %>% 
  rename(Date = date, HouseValue = value) %>% 
  select(Date, HouseValue) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

```

## All-Transactions House Price Index for the United States NOT FINISHED, NEED TO ADD INSTEAD OF HOUSE PRICES AND INTERPOLATE
```{r}

# FRED All-Transactions House Price Index for the United States 
house_price_index <- Quandl("FRED/USSTHPI", start_date=SDate,end_date=EDate, collapse = "monthly") %>% 
  rename(HousePriceIndex = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))
```

## Retail Sales
```{r}

# FRED retail sales
retail_sales <- Quandl("FRED/RSXFS", start_date=SDate,end_date=EDate, collapse = "monthly") %>% 
  rename(RetailSales = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))
```

## All Employees, Retail Trade
```{r}

# FRED All Employees, Retail Trade
retail_trade <- Quandl("FRED/USTRADE", start_date=SDate,end_date=EDate, collapse = "monthly") %>% 
  rename(RetailTrade = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

```

## Interest rates
```{r}

# T-Bills
threemonths_IR <- Quandl("FRED/DTB3", start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  rename(ThreemonthsIR = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

# Five-y Bonds
fiveyears_IR <- Quandl("FRED/DGS5", start_date=SFDate, end_date=EFDate, collapse = "monthly") %>% 
  rename(FiveyearsIR = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

# Ten-y Bonds
tenyears_IR <- Quandl("FRED/DGS10", start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
   rename(TenyearsIR = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))
  
# Thirty-y Bonds
thirtyyears_IR <- Quandl("FRED/DGS30", start_date=SFDate, end_date=EFDate, collapse = "monthly") %>% 
  rename(ThirtyyearsIR = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

## Interest spreads

# Five years three months spread
#Spread5.3 <- DGS5 - threemonths ##
```

## Building permits
```{r}

# FRED Building Permits
building_permits <- Quandl("FRED/PERMIT", start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  rename(BuildingPermits = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

```

## Consumer sentiment
```{r}

# Index of consumer sentiment
consumer_sentiment <- Quandl("UMICH/SOC1",start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  rename(ConsumerSentiment = Index) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

```

## Average weekly hours of manufacturing
```{r}

# FRED average weekly hours of manufacturing
avg_weekly_hours_man <- Quandl("FRED/AWHAEMAN", start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  rename(AvgWeeklyHoursMan = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

```

## Average Weekly Hours of Production and Nonsupervisory Employees, Manufacturing
```{r}

# FRED average weekly hours of Production and Nonsupervisory Employees, Manufacturing
avg_weekly_hours_prod <- Quandl("FRED/AWHMAN", start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  rename(AvgWeeklyHoursProd = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))
```

## Manufacturers new orders
```{r}

# FRED manufacturers new orders.
new_orders_man <- Quandl("FRED/AMTMNO", start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  rename(NewOrdersMan = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))
```

## Future New Orders; Diffusion Index for Federal Reserve District 3: Philadelphia
```{r}

# FRED Future New Orders; Diffusion Index for Federal Reserve District 3: Philadelphia
future_new_orders <- Quandl("FRED/NOFDFSA066MSFRBPHI", start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  rename(FutureNewOrders = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))
```

# Coincident Indicators
* Industrial production Index
* Real Personal incomes
* Manufacturing and trade sales

## Industrial production
```{r}

# Industrial Production Index
ind_prod_ind <- Quandl("FRED/INDPRO", start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  rename(IndProdInd = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

```

##
```{r}

# Real median household income
med_house_income <- Quandl("FRED/MEHOINUSA672N", 
                           start_date=SFDate, 
                           end_date=EFDate ,
                           collapse = "monthly")

# Real disposable personal income
disp_pers_income <- Quandl("FRED/DSPIC96", start_date=SFDate, end_date=EFDate, collapse = "monthly") %>% 
  rename(DispPersIncome = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

# Personal consumption expenditures
pers_cons_exp <- Quandl("FRED/PCE", 
                        start_date=SFDate, 
                        end_date=EFDate ,
                        collapse = "monthly")

# Personal consumption expenditures on durable goods
pers_cons_exp_durable <- Quandl("FRED/PCEDG", 
                                start_date=SFDate,
                                end_date=EFDate,
                                collapse = "monthly")
# Personal savings rate
pers_save_rate <- Quandl("FRED/PSAVERT", 
                         start_date=SFDate, 
                         end_date=EFDate,
                         collapse = "monthly")

# Retail and food sales
ret_food_sales <- Quandl("FRED/RRSFS",
                                 start_date=SFDate, 
                                 end_date=EFDate ,
                                 collapse = "monthly")


```

## Real manufacturing and trade sales
```{r}

# FRED Manufacturing and trade sales
man_trade_sales <- Quandl("FRED/CMRMTSPL", start_date=SFDate, end_date=EFDate ,collapse = "monthly") %>% 
  rename(ManTradeSales = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

```

# Lagging indicators
* Real GDP growth
* Average duration of unemployment 
* Inventory to sales ratio
* Change in unit labor costs 
* Inflation
* Average prime lending rate 
* Ratio of consumer installment debt to income
* Commercial and industrial loans 
* Outstanding loans
* Dollar index

## Real GDP growth
```{r}

# Real GDP
GDP_real <- Quandl("FRED/GDPC1", 
                   start_date=SFDate, 
                   end_date=EFDate, 
                   collapse = "monthly")

GDP_real_growth <- GDP_real %>% 
  tq_transmute(select = Value,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "GDP Growth")
  
```

## Employment
```{r}

# Unemployment rate
un_rate <- Quandl("FRED/UNRATE", 
                 start_date=SFDate, 
                 end_date=EFDate ,
                 collapse = "monthly")

# Natural rate of unemployment long term
nat_un_lt <- Quandl("FRED/NROU", 
                    start_date=SFDate, 
                    end_date=EFDate ,
                    collapse = "monthly")

# Natural rate of unemployment short term
nat_un_st <- Quandl("FRED/NROUST", 
                    start_date=SFDate, 
                    end_date=EFDate ,
                    collapse = "monthly")

# Civilian employment population ratio
em_ratio <- Quandl("FRED/EMRATIO", 
                  start_date=SFDate, 
                  end_date=EFDate ,
                  collapse = "monthly")

# Unemployed
unemployment <- Quandl("FRED/UNEMPLOY", 
                       start_date=SFDate, 
                       end_date=EFDate ,
                       collapse = "monthly")

# Total non farm employed
tot_non_farm_employed <- Quandl("FRED/PAYEMS",
                                start_date=SFDate, 
                                end_date=EFDate ,
                                collapse = "monthly")

# Total manufacturing employed
tot_man_employed <- Quandl("FRED/MANEMP",
                           start_date=SFDate, 
                           end_date=EFDate ,
                           collapse = "monthly")

# Initial claims
initial_claims <- Quandl("FRED/ICSA", 
                         start_date=SFDate, 
                         end_date=EFDate ,
                         collapse = "monthly")

# Average duration of unemployment
avg_dur_unem <- Quandl('FRED/UEMPMEAN', start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  rename(AvgDurUnem = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

# Unit labor costs
un_labor_costs <- Quandl('FRED/PRS30006111', 
                         start_date=SDate, 
                         end_date=EDate, 
                         collapse = "monthly")
```

## Inventories to sales ratio
```{r}

# Retail inventories to sales
retail_inv_to_sales <- Quandl("FRED/RETAILIRSA", 
                              start_date=SFDate, 
                              end_date=EFDate ,
                              collapse = "monthly")

# Manufacturing inventories to sales
manufacturing_inv_to_sales <- Quandl("FRED/MNFCTRIRSA", 
                                     start_date=SFDate, 
                                     end_date=EFDate ,
                                     collapse = "monthly")

# Total inventories to sales
total_inv_to_sales <- Quandl("FRED/ISRATIO", start_date=SFDate, end_date=EFDate, collapse = "monthly") %>% 
  rename(TotalInvToSales = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

```

## Inflation
```{r}

# Core inflation
core_CPI <- Quandl("FRED/CPILFESL", start_date=SFDate, end_date=EFDate, collapse = "monthly") %>% 
  rename(CoreCPI = Value)

# Inflation
CPI <- Quandl("FRED/CPIAUCSL", start_date=SFDate, end_date=EFDate , collapse = "monthly") %>% 
   rename(CPI = Value)

# Year over year inflation
CPI <- CPI %>% 
  group_by(month=month(Date)) %>%
  arrange(Date) %>%
  mutate(YOYCPI=CPI/lag(CPI,1)-1)

# Year over year core inflation
core_CPI <- core_CPI %>% 
  group_by(month=month(Date)) %>%
  arrange(Date) %>%
  mutate(YOYCoreCPI=CoreCPI/lag(CoreCPI,1)-1)

# Core inflation spread
YOYCoreCPI <- CPI %>% 
  left_join(core_CPI, by="Date") %>% 
  mutate(spread = YOYCPI - YOYCoreCPI) %>% 
  select(Date, YOYCoreCPI) %>% 
  mutate(Date = floor_date(Date, unit = "month")) %>% 
  na.omit()
```

## Consumer debt to income
```{r}

# FRED consumer debt to income
consumer_debt_to_income <- Quandl("FRED/TDSP",start_date=SFDate, end_date=EFDate, collapse = "monthly") %>% 
  rename(ConsumerDebtToIncome = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))
```

## Commercial and industrial loans
```{r}

# All commercial banks
comm_ind_loans_all_banks <- Quandl("FRED/TOTCI", start_date=SFDate, end_date=EFDate, collapse = "monthly") %>% 
  rename(CommNndLoansAllBanks = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

# Prime lending rate
prime_lend_rate <- Quandl('FRED/DPRIME', start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  rename(PrimeLendRate = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))
```

## Outstanding loans
```{r}

# FRED Outstanding loans
outstanding_loans <- Quandl("FRED/TOTLL", start_date=SFDate, end_date=EFDate, collapse = "monthly") %>% 
  rename(OutstandingLoans = Value) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

```

## Dollar index
```{r}

#Trade weighted dollar index
dollar_index <- tq_get("DX-Y.NYB",
                       get = "stock.prices",
                       from = "1920-01-01")

#Trade weighted dollar index growth
dollar_index <- dollar_index %>%
  tq_transmute(select = adjusted,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "Index_growth")
```

# Other economic indicators
* Total public debt
* Total public debt to GDP
* Excess reserves

```{r}

# Federal Debt: Total Public Debt
total_public_debt <- Quandl("FRED/GFDEBTN", 
                            start_date=SFDate, 
                            end_date=EFDate ,
                            collapse = "monthly")

# Federal Debt: Total Public Debt as Percent of Gross Domestic Product
total_public_debt_to_GDP <- Quandl("FRED/GFDEGDQ188S", 
                                   start_date=SFDate, 
                                   end_date=EFDate ,
                                   collapse = "monthly")

# Excess Reserves of Depository Institutions
excess_reserves <- Quandl("FRED/EXCSRESNW", 
                          start_date=SFDate, 
                          end_date=EFDate ,
                          collapse = "monthly")

```

# FINAL DATA FRAME
```{r}
data_all <- merge.data.frame(avg_dur_unem, #NE DELA
                             avg_weekly_hours_man, 
                             building_permits,
                             comm_ind_loans_all_banks,
                             consumer_debt_to_income,
                             consumer_sentiment,
                             core_CPI,
                             disp_pers_income,
                             dollar_index,
                             em_ratio,
                             fiveyears_IR,
                             GDP_real_growth,
                             house_values,
                             ind_prod_ind,
                             initial_claims,
                             man_trade_sales,
                             manufacturing_inv_to_sales,
                             med_house_income,
                             new_orders_man,
                             outstanding_loans,
                             pers_cons_exp,
                             pers_save_rate,
                             prime_lend_rate,
                             ret_food_sales,
                             retail_inv_to_sales,
                             retail_sales,
                             SP500_Div,
                             SP500_Div_Yield,
                             SP500_Earnings,
                             SP500_PE,
                             stockmarket_returns,
                             tenyears_IR,
                             thirtyyears_IR,
                             threemonths_IR,
                             tot_man_employed,
                             tot_non_farm_employed,
                             total_inv_to_sales,
                             total_public_debt_to_GDP,
                             un_rate,
                             unemployment,
                             by = "Date")
```

```{r}
#join the three data frames
dataAll <- stockmarket_returns %>%
    left_join(house_price_index, by='Date') %>%
    left_join(retail_trade, by='Date') %>% 
    left_join(building_permits, by='Date') %>% 
    left_join(consumer_sentiment, by='Date') %>% 
    left_join(avg_weekly_hours_prod, by='Date') %>% 
    left_join(future_new_orders, by='Date') %>% 
    left_join(threemonths_IR, by='Date') %>% 
    left_join(fiveyears_IR, by='Date') %>% 
    left_join(tenyears_IR, by='Date') %>% 
    left_join(thirtyyears_IR, by='Date') %>% 
    left_join(ind_prod_ind, by='Date') %>% 
    left_join(disp_pers_income, by='Date') %>% 
    left_join(man_trade_sales, by='Date') %>% 
    left_join(total_inv_to_sales, by='Date') %>% 
    left_join(avg_dur_unem, by='Date') %>% 
    left_join(YOYCoreCPI, by='Date') %>% 
    left_join(prime_lend_rate, by='Date') %>% 
    #left_join(consumer_debt_to_income, by='Date') %>% 
    left_join(comm_ind_loans_all_banks, by='Date') %>% 
    left_join(outstanding_loans, by='Date')
```

```{r}
dataAllInterpolated <- dataAll %>% 
  mutate(HousePriceIndex = na.spline(HousePriceIndex))%>% 
  na.omit()
```


```{r}
dataAllPctChange <- dataAll %>% 
  mutate(SP500Returns_pct_change = (SP500Returns/lag(SP500Returns) - 1)) %>% 
  mutate(HousePriceIndex_pct_change = (HousePriceIndex/lag(HousePriceIndex) - 1)) %>% 
  mutate(RetailTrade_pct_change = (RetailTrade/lag(RetailTrade) - 1)) %>% 
  mutate(BuildingPermits_pct_change = (BuildingPermits/lag(BuildingPermits) - 1)) %>% 
  mutate(ConsumerSentiment_pct_change = (ConsumerSentiment/lag(ConsumerSentiment) - 1)) %>% 
  mutate(AvgWeeklyHoursProd_pct_change = (AvgWeeklyHoursProd/lag(AvgWeeklyHoursProd) - 1)) %>% 
  mutate(FutureNewOrders_pct_change = (FutureNewOrders/lag(FutureNewOrders) - 1)) %>% 
  mutate(ThreemonthsIR_pct_change = (ThreemonthsIR/lag(ThreemonthsIR) - 1)) %>% 
  mutate(FiveyearsIR_pct_change = (FiveyearsIR/lag(FiveyearsIR) - 1)) %>% 
  mutate(TenyearsIR_pct_change = (TenyearsIR/lag(TenyearsIR) - 1)) %>% 
  mutate(ThirtyyearsIR_pct_change = (ThirtyyearsIR/lag(ThirtyyearsIR) - 1)) %>% 
  mutate(IndProdInd_pct_change = (IndProdInd/lag(IndProdInd) - 1)) %>% 
  mutate(DispPersIncome_pct_change = (DispPersIncome/lag(DispPersIncome) - 1)) %>% 
  mutate(ManTradeSales_pct_change = (ManTradeSales/lag(ManTradeSales) - 1)) %>% 
  mutate(TotalInvToSales_pct_change = (TotalInvToSales/lag(TotalInvToSales) - 1)) %>% 
  mutate(AvgDurUnem_pct_change = (AvgDurUnem/lag(AvgDurUnem) - 1)) %>% 
  mutate(YOYCoreCPI_pct_change = (YOYCoreCPI/lag(YOYCoreCPI) - 1)) %>% 
  mutate(PrimeLendRate_pct_change = (PrimeLendRate/lag(PrimeLendRate) - 1)) %>% 
  mutate(CommNndLoansAllBanks_pct_change = (CommNndLoansAllBanks/lag(CommNndLoansAllBanks) - 1)) %>% 
  mutate(OutstandingLoans_pct_change = (OutstandingLoans/lag(OutstandingLoans) - 1)) %>% 
  mutate(CommNndLoansAllBanks_pct_change = (CommNndLoansAllBanks/lag(CommNndLoansAllBanks) - 1)) %>% 
  mutate(CommNndLoansAllBanks_pct_change = (CommNndLoansAllBanks/lag(CommNndLoansAllBanks) - 1)) %>% 
  na.omit()
```

```{r}
  write_csv(dataAll, "mergedData.csv")
  write_csv(dataAllPctChange, "mergedDataPctChange.csv")
```

```{r}
exportcluster <- read_csv("Desktop/masterThesis/investmentfound/exportcluster.csv")

clusterdata <- exportcluster %>% 
  select(cluster)

dataAllPctChangeCluster <- dataAllPctChange %>% 
  mutate(cluster = clusterdata)


dataAllPctChangeCluster <- cbind(dataAllPctChange, clusterdata)

dataAllPctChangeCluster %>%
  ggplot(aes(x = Date, y = TenyearsIR)) +
  geom_point(aes (color = factor (cluster)), size = 1)
 
```

