---
title: "Data fetching"
output: html_document
date: "2022-12-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(anytime)
library(lubridate)
library(timechange)
library(xts)
library(zoo)
library(Quandl)
library(forecast)
library(tidyverse)
library(ggplot2)
library(rlang)
library(PortfolioAnalytics)
library(PerformanceAnalytics)
library(quantmod)
library(TTR)
library(tidyquant)
library(timetk)

```

```{r}
Quandl.api_key("YE-L2_sxPkntzGfHo3vZ")
EDate <- as.Date(Sys.Date())
SDate <- as.Date(EDate-365*100)
YoY <- as.Date(EDate-365)

EDate
EFDate <- as.Date(Sys.Date())
SFDate <- EFDate - 365*100
SFDate
EFDate
```

#Leading indicators are
* Stock market
* House prices
* Retail Sales
* Interest spread (LT & ST bonds)
* Building Permits
* Consumer expectations
* Average weekly hours (manufacturing)
* Manufacturers new orders.

## Stock market
```{r}
# S&P500 Prices
stockmarket <- tq_get("^GSPC",
                      from ="1920-01-01",
                      get = "stock.prices")

# S&P500 Returns
stockmarket_returns <- stockmarket %>%
  tq_transmute(select = adjusted,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "SP500_returns")

# S&P500 Dividends
SP500_Div <- Quandl('MULTPL/SP500_DIV_MONTH', 
              start_date=SDate, 
              end_date=EDate)

# S&P500 Dividend Yield
SP500_Div_Yield <- Quandl('MULTPL/SP500_DIV_YIELD_MONTH', 
                   start_date=SDate, 
                   end_date=EDate)

# S&P500 PE Ratios
SP500_PE <- Quandl('MULTPL/SP500_PE_RATIO_MONTH', 
             start_date=SDate, 
             end_date=EDate)

# S&P500 Earnings
SP500_Earnings <- Quandl('MULTPL/SP500_EARNINGS_MONTH', 
                        start_date=SDate, 
                        end_date=EDate)

#PayoutRatio <- Div$Value/SP500Earnings$Value ##


```

## House prices
```{r}

# Zillow home values index
house_values <- Quandl.datatable("ZILLOW/DATA", 
                                 indicator_id="ZALL",
                                 region_id="102001")

```

## Retail Sales
```{r}

# FRED retail sales
retail_sales <- Quandl("FRED/RSXFS",
                       start_date=SDate, 
                       end_date=EDate ,
                       collapse = "monthly")

```

## Interest rates
```{r}

# T-Bills
threemonths_IR <- Quandl("FRED/DTB3",
                         start_date=SDate, 
                         end_date=EDate, 
                         collapse = "monthly")

# Five-y Bonds
fiveyears_IR <- Quandl("FRED/DGS5", 
                       start_date=SFDate, 
                       end_date=EFDate, 
                       collapse = "monthly")

# Ten-y Bonds
tenyears_IR <- Quandl("FRED/DGS10",
                      start_date=SDate, 
                      end_date=EDate,
                      collapse = "monthly")
# Thirty-y Bonds
thirtyyears_IR <- Quandl("FRED/DGS30",
                          start_date=SFDate,
                          end_date=EFDate ,
                          collapse = "monthly")

## Interest spreads

# Five years three months spread
#Spread5.3 <- DGS5 - threemonths ##
```

## Building permits
```{r}

# FRED Building Permits
building_permits <- Quandl("FRED/PERMIT",
                           start_date=SDate,
                           end_date=EDate,
                           collapse = "monthly")

```

## Consumer sentiment
```{r}

# Index of consumer sentiment
consumer_sentiment <- Quandl("UMICH/SOC1", 
                             start_date=SDate, 
                             end_date=EDate,
                             collapse = "monthly")

```

## Average weekly hours of manufacturing
```{r}

# FRED average weekly hours of manufacturing
avg_weekly_hours_man <- Quandl("FRED/AWHAEMAN", 
                               start_date=SDate, 
                               end_date=EDate,
                               collapse = "monthly")

```

## Manufacturers new orders
```{r}

# FRED manufacturers new orders.
new_orders_man <- Quandl("FRED/AMTMNO",
                         start_date=SDate, 
                         end_date=EDate,
                         collapse = "monthly")

```

# Coincident Indicators
* Industrial production Index
* Real Personal incomes
* Manufacturing and trade sales

## Industrial production
```{r}

# Industrial Production Index
ind_prod_ind <- Quandl("FRED/INDPRO", 
                       start_date=SDate, 
                       end_date=EDate,
                       collapse = "monthly")

```

##
```{r}

# Real median household income
med_house_income <- Quandl("FRED/MEHOINUSA672N", 
                           start_date=SFDate, 
                           end_date=EFDate ,
                           collapse = "monthly")

# Real disposable personal income
disp_pers_income <- Quandl("FRED/DSPIC96", 
                           start_date=SFDate, 
                           end_date=EFDate ,
                           collapse = "monthly")

# Personal consumption expenditures
pers_cons_exp <- Quandl("FRED/PCE", 
                        start_date=SFDate, 
                        end_date=EFDate ,
                        collapse = "monthly")

# Personal consumption expenditures on durable goods
pers_cons_exp_durable <- Quandl("FRED/PCEDG", 
                                start_date=SFDate,
                                end_date=EFDate,
                                collapse = "monthly")
# Personal savings rate
pers_save_rate <- Quandl("FRED/PSAVERT", 
                         start_date=SFDate, 
                         end_date=EFDate,
                         collapse = "monthly")

# Retail and food sales
ret_food_sales <- Quandl("FRED/RRSFS",
                                 start_date=SFDate, 
                                 end_date=EFDate ,
                                 collapse = "monthly")


```

## Real manufacturing and trade sales
```{r}

# FRED Manufacturing and trade sales
man_trade_sales <- Quandl("FRED/CMRMTSPL", 
                          start_date=SFDate, 
                          end_date=EFDate ,
                          collapse = "monthly" )

```

# Lagging indicators
* Real GDP growth
* Average duration of unemployment 
* Inventory to sales ratio
* Change in unit labor costs 
* Inflation
* Average prime lending rate 
* Ratio of consumer installment debt to income
* Commercial and industrial loans 
* Outstanding loans
* Dollar index

## Real GDP growth
```{r}

# Real GDP
GDP_real <- Quandl("FRED/GDPC1", 
                   start_date=SFDate, 
                   end_date=EFDate, 
                   collapse = "monthly")

GDP_real_growth <- GDP_real %>% 
  tq_transmute(select = Value,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "GDP Growth")
  
```

## Employment
```{r}

# Unemployment rate
un_rate <- Quandl("FRED/UNRATE", 
                 start_date=SFDate, 
                 end_date=EFDate ,
                 collapse = "monthly")

# Natural rate of unemployment long term
nat_un_lt <- Quandl("FRED/NROU", 
                    start_date=SFDate, 
                    end_date=EFDate ,
                    collapse = "monthly")

# Natural rate of unemployment short term
nat_un_st <- Quandl("FRED/NROUST", 
                    start_date=SFDate, 
                    end_date=EFDate ,
                    collapse = "monthly")

# Civilian employment population ratio
em_ratio <- Quandl("FRED/EMRATIO", 
                  start_date=SFDate, 
                  end_date=EFDate ,
                  collapse = "monthly")

# Unemployed
unemployment <- Quandl("FRED/UNEMPLOY", 
                       start_date=SFDate, 
                       end_date=EFDate ,
                       collapse = "monthly")

# Total non farm employed
tot_non_farm_employed <- Quandl("FRED/PAYEMS",
                                start_date=SFDate, 
                                end_date=EFDate ,
                                collapse = "monthly")

# Total manufacturing employed
tot_man_employed <- Quandl("FRED/MANEMP",
                           start_date=SFDate, 
                           end_date=EFDate ,
                           collapse = "monthly")

# Initial claims
initial_claims <- Quandl("FRED/ICSA", 
                         start_date=SFDate, 
                         end_date=EFDate ,
                         collapse = "monthly")

# Average duration of unemployment
avg_dur_unem <- Quandl('FRED/UEMPMEAN', 
                       start_date=SDate, 
                       end_date=EDate,
                       collapse = "monthly")

# Unit labor costs
un_labor_costs <- Quandl('FRED/PRS30006111', 
                         start_date=SDate, 
                         end_date=EDate, 
                         collapse = "monthly")
```

## Inventories to sales ratio
```{r}

# Retail inventories to sales
retail_inv_to_sales <- Quandl("FRED/RETAILIRSA", 
                              start_date=SFDate, 
                              end_date=EFDate ,
                              collapse = "monthly")

# Manufacturing inventories to sales
manufacturing_inv_to_sales <- Quandl("FRED/MNFCTRIRSA", 
                                     start_date=SFDate, 
                                     end_date=EFDate ,
                                     collapse = "monthly")

# Total inventories to sales
total_inv_to_sales <- Quandl("FRED/ISRATIO", 
                             start_date=SFDate, 
                             end_date=EFDate ,
                             collapse = "monthly")

```

## Inflation
```{r}

# Core inflation
core_CPI <- Quandl("FRED/CPILFESL", 
                   start_date=SFDate, 
                   end_date=EFDate, 
                   collapse = "monthly")

# Inflation
CPI <- Quandl("FRED/CPIAUCSL", 
              start_date=SFDate, 
              end_date=EFDate , 
              collapse = "monthly")

# Year over year inflation
CPI$Date  <- as.POSIXct(CPI$Date)

CPI <- CPI %>% 
  group_by(month=month(Date)) %>%
  arrange(Date) %>%
  mutate(yearOverYear=Value/lag(Value,1)-1)

# Year over year core inflation
core_CPI$Date  <- as.POSIXct(core_CPI$Date)

core_CPI <- core_CPI %>% 
  group_by(month=month(Date)) %>%
  arrange(Date) %>%
  mutate(yearOverYear=Value/lag(Value,1)-1)

# Core inflation spread
CPI_spread <- merge.data.frame(CPI, core_CPI, by = "Date")

spread <- CPI_spread$yearOverYear.x - CPI_spread$yearOverYear.y

CPI_spread$spread <- spread

```

## Consumer debt to income
```{r}

# FRED consumer debt to income
consumer_debt_to_income <- Quandl("FRED/TDSP", 
                                  start_date=SFDate, 
                                  end_date=EFDate ,
                                  collapse = "monthly")

```

## Commercial and industrial loans
```{r}

# All commercial banks
comm_ind_loans_all_banks <- Quandl("FRED/TOTCI", 
                                   start_date=SFDate, 
                                   end_date=EFDate ,
                                   collapse = "monthly")

# Prime lending rate
prime_lend_rate <- Quandl('FRED/DPRIME', 
                          start_date=SDate, 
                          end_date=EDate,
                          collapse = "monthly")
```

## Outstanding loans
```{r}

# FRED Outstanding loans
outstanding_loans <- Quandl("FRED/TOTLL", 
                            start_date=SFDate, 
                            end_date=EFDate ,
                            collapse = "monthly")

```

## Dollar index
```{r}

#Trade weighted dollar index
dollar_index <- tq_get("DX-Y.NYB",
                       get = "stock.prices",
                       from = "1920-01-01")

#Trade weighted dollar index growth
dollar_index <- dollar_index %>%
  tq_transmute(select = adjusted,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "Index_growth")
```

# Other economic indicators
* Total public debt
* Total public debt to GDP
* Excess reserves

```{r}

# Federal Debt: Total Public Debt
total_public_debt <- Quandl("FRED/GFDEBTN", 
                            start_date=SFDate, 
                            end_date=EFDate ,
                            collapse = "monthly")

# Federal Debt: Total Public Debt as Percent of Gross Domestic Product
total_public_debt_to_GDP <- Quandl("FRED/GFDEGDQ188S", 
                                   start_date=SFDate, 
                                   end_date=EFDate ,
                                   collapse = "monthly")

# Excess Reserves of Depository Institutions
excess_reserves <- Quandl("FRED/EXCSRESNW", 
                          start_date=SFDate, 
                          end_date=EFDate ,
                          collapse = "monthly")

```

# FINAL DATA FRAME
```{r}
data_all <- merge.data.frame(avg_dur_unem, 
                             avg_weekly_hours_man, 
                             building_permits,
                             comm_ind_loans_all_banks,
                             consumer_debt_to_income,
                             consumer_sentiment,
                             core_CPI,
                             disp_pers_income,
                             dollar_index,
                             em_ratio,
                             fiveyears_IR,
                             GDP_real_growth,
                             house_values,
                             ind_prod_ind,
                             initial_claims,
                             man_trade_sales,
                             manufacturing_inv_to_sales,
                             med_house_income,
                             new_orders_man,
                             outstanding_loans,
                             pers_cons_exp,
                             pers_save_rate,
                             prime_lend_rate,
                             ret_food_sales,
                             retail_inv_to_sales,
                             retail_sales,
                             SP500_Div,
                             SP500_Div_Yield,
                             SP500_Earnings,
                             SP500_PE,
                             stockmarket_returns,
                             tenyears_IR,
                             thirtyyears_IR,
                             threemonths_IR,
                             tot_man_employed,
                             tot_non_farm_employed,
                             total_inv_to_sales,
                             total_public_debt_to_GDP,
                             un_rate,
                             unemployment,
                             by = "Date")
```

```{r}
data_all <- merge.data.frame(stockmarket_returns,
                             house_values,
                             retail_sales,
                             building_permits,
                             consumer_sentiment,
                             avg_weekly_hours_man,
                             new_orders_man,
                             threemonths_IR,
                             fiveyears_IR,
                             tenyears_IR,
                             thirtyyears_IR,
                             ind_prod_ind,
                             disp_pers_income,
                             man_trade_sales,
                             total_inv_to_sales,
                             avg_dur_unem,
                             core_CPI,
                             prime_lend_rate,
                             consumer_debt_to_income,
                             comm_ind_loans_all_banks,
                             outstanding_loans,
                             by = "Date"
                             )
```

