---
title: "Data fetching"
output: html_document
date: "2022-12-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(anytime)
library(lubridate)
library(timechange)
library(xts)
library(zoo)
library(Quandl)
library(forecast)
library(tidyverse)
library(ggplot2)
library(rlang)
library(PortfolioAnalytics)
library(PerformanceAnalytics)
library(quantmod)
library(TTR)
library(tidyquant)
library(timetk)
```

```{r}
Quandl.api_key("YE-L2_sxPkntzGfHo3vZ")
EDate <- as.Date(Sys.Date())
SDate <- as.Date(EDate-365*100)
YoY <- as.Date(EDate-365)

EFDate <- as.Date(Sys.Date())
SFDate <- EFDate - 365*100
```

#Leading indicators are
* Stock market
* House prices
* Retail Trade
* Interest spread (LT & ST bonds)
* Building Permits
* Consumer sentiment
* Average weekly hours (manufacturing)
* Future new orders

## Stock market
```{r}
# S&P500 Prices
stockmarket <- tq_get("^GSPC",
                      from = SDate,
                      get = "stock.prices") %>% 
  tq_transmute(select = adjusted, mutate_fun = to.monthly, indexAt = "firstof")%>% 
  rename(Date = date)

# S&P500 Returns
stockmarket_returns <- stockmarket %>%
  tq_transmute(select = adjusted,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "SP500Returns")
```

## All-Transactions House Price Index for the United States
```{r}

# FRED All-Transactions House Price Index for the United States 
house_price_index <- tq_get("USSTHPI",
                            from = SDate,
                            "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(HousePriceIndex = price)%>% 
  rename(Date = date)
```

## All Employees, Retail Trade
```{r}

# FRED All Employees, Retail Trade
retail_trade <- tq_get("USASARTMISMEI", 
                            from =SDate, 
                            get = "economic.data")%>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(RetailTrade = price) %>% 
  rename(Date = date)
```

## Interest rates
```{r}

# T-Bills
threemonths_IR <- tq_get("DTB3",
                         from = SDate,
                         "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(ThreemonthsIR = price) %>% 
  rename(Date = date)

# Five-y Bonds
fiveyears_IR <-  tq_get("DGS5",
                         from = SDate,
                         "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(FiveyearsIR = price) %>% 
  rename(Date = date)

# Ten-y Bonds
tenyears_IR <-  tq_get("DGS10",
                         from = SDate,
                         "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(TenyearsIR = price) %>% 
  rename(Date = date)
  
# Thirty-y Bonds
thirtyyears_IR <- tq_get("DGS30",
                         from = SDate,
                         "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(ThirtyyearsIR = price) %>% 
  rename(Date = date)

# 30y - 3m spread

IR_Spread <- thirtyyears_IR %>%
    left_join(threemonths_IR, by='Date') %>% 
  mutate(IRSpread = ThirtyyearsIR - ThreemonthsIR) %>% 
  select(-ThirtyyearsIR, -ThreemonthsIR)
```

## Building permits
```{r}

# FRED Building Permits
building_permits <-  tq_get("PERMIT",
                         from = SDate,
                         "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(BuildingPermits = price) %>% 
  rename(Date = date)
```

## Consumer sentiment
```{r}

# Index of consumer sentiment
consumer_sentiment <- Quandl("UMICH/SOC1",start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  rename(ConsumerSentiment = Index) %>% 
  mutate(Date = floor_date(Date, unit = "month"))
```

## Average Weekly Hours of Production and Nonsupervisory Employees, Manufacturing
```{r}

# FRED average weekly hours of Production and Nonsupervisory Employees, Manufacturing
avg_weekly_hours_prod <- tq_get("AWHMAN", 
                            from =SDate, 
                            get = "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(AvgWeeklyHoursProd = price) %>% 
  rename(Date = date)
```

## Future New Orders; Diffusion Index for Federal Reserve District 3: Philadelphia
```{r}

# FRED Future New Orders; Diffusion Index for Federal Reserve District 3: Philadelphia
future_new_orders <- tq_get("NOFDFSA066MSFRBPHI", 
                            from =SDate, 
                            get = "economic.data")%>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(FutureNewOrders = price) %>% 
  rename(Date = date)
```

# Coincident Indicators
* Industrial production Index
* Real Personal incomes
* Manufacturing and trade sales

## Industrial production
```{r}

# Industrial Production Index
ind_prod_ind <- tq_get("INDPRO", 
                            from =SDate, 
                            get = "economic.data")%>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(IndProdInd = price) %>% 
  rename(Date = date)
```

## Real disposable personal income
```{r}
# Real disposable personal income
disp_pers_income <- tq_get("DSPIC96", 
                            from ="1920-01-01", 
                            get = "economic.data")%>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(DispPersIncome = price) %>% 
  rename(Date = date)
```

## Real manufacturing and trade sales
```{r}

# FRED Manufacturing and trade sales
man_trade_sales <- tq_get("CMRMTSPL", 
                            from =SDate, 
                            get = "economic.data")%>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(ManTradeSales = price) %>% 
  rename(Date = date)
```

# Lagging indicators
* Real GDP growth
* Average duration of unemployment 
* Inventory to sales ratio
* Inflation
* Average prime lending rate 
* Ratio of consumer installment debt to income
* Commercial and industrial loans 
* Outstanding loans
* Dollar index

## Real GDP #LAG one to three quarters
```{r}

# Real GDP
GDP_real <- tq_get("GDPC1", 
                            from =SDate, 
                            get = "economic.data")%>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(RealGDP = price) %>% 
  rename(Date = date)
```

## Employment #Lag a few quarters
```{r}

# Average duration of unemployment
avg_dur_unem <- tq_get("UEMPMEAN", 
                            from =SDate, 
                            get = "economic.data")%>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(AvgDurUnem = price) %>% 
  rename(Date = date)
```

## Inventories to sales ratio ### Remember to change directory
```{r}

# Total inventories to sales ratio
inv_to_sales <- read_csv("invtosales.csv", col_types = cols(Date = col_date(format = "%Y-%m-%d")))
```

## Inflation
```{r}

# Core inflation
core_CPI <- tq_get("CPILFESL", 
                            from =SDate, 
                            get = "economic.data")%>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(CoreCPI = price) %>% 
  rename(Date = date)

# Year over year core inflation
core_CPI_YoY <- core_CPI %>%
  arrange(Date) %>%
  mutate(YOYCoreCPI=CoreCPI/lag(CoreCPI,12)-1) %>% 
  select(-CoreCPI)
```

## Consumer debt to income
```{r}

# FRED consumer debt to income
consumer_debt_to_income <- tq_get("TDSP", 
                            from =SDate, 
                            get = "economic.data")%>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(ConsumerDebtToIncome = price) %>% 
  rename(Date = date)
```

## Commercial and industrial loans & Prime lending rate
```{r}

# All commercial banks
comm_ind_loans_all_banks <- tq_get("TOTCI", 
                            from =SDate, 
                            get = "economic.data")%>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(CommNndLoansAllBanks = price) %>% 
  rename(Date = date)

# Prime lending rate
prime_lend_rate <- tq_get("DPRIME", 
                            from =SDate, 
                            get = "economic.data")%>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(PrimeLendRate = price) %>% 
  rename(Date = date)
```

## Outstanding loans
```{r}

# FRED Outstanding loans
outstanding_loans <- tq_get("TOTLL", 
                            from =SDate, 
                            get = "economic.data")%>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(OutstandingLoans = price) %>% 
  rename(Date = date)
```

## Dollar index
```{r}

#Trade weighted dollar index
dollar_index <- tq_get("DX-Y.NYB",
                       get = "stock.prices",
                       from = SDate) %>% 
  tq_transmute(select = adjusted, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(DollarValueIndex = adjusted) %>% 
  rename(Date = date)

#Trade weighted dollar index growth
dollar_index_growth <- dollar_index %>%
  tq_transmute(select = DollarValueIndex,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "Index_growth")%>% 
  rename(DollarIndex = Index_growth)
```


```{r}
#join the three data frames
dataAll <- stockmarket_returns %>%
    left_join(house_price_index, by='Date') %>%
    left_join(retail_trade, by='Date') %>% 
    left_join(IR_Spread, by='Date') %>% 
    left_join(building_permits, by='Date') %>%
    left_join(consumer_sentiment, by='Date') %>% 
    left_join(avg_weekly_hours_prod, by='Date') %>% 
    left_join(future_new_orders, by='Date') %>% 
    left_join(dollar_index_growth, by='Date') %>% 
    left_join(threemonths_IR, by='Date') %>% 
    left_join(fiveyears_IR, by='Date') %>% 
    left_join(tenyears_IR, by='Date') %>% 
    left_join(thirtyyears_IR, by='Date') %>% 
    left_join(ind_prod_ind, by='Date') %>% 
    left_join(disp_pers_income, by='Date') %>%
    left_join(GDP_real, by='Date') %>% 
    left_join(man_trade_sales, by='Date') %>% 
    left_join(inv_to_sales, by='Date') %>% 
    left_join(avg_dur_unem, by='Date') %>% 
    left_join(core_CPI_YoY, by='Date') %>% 
    left_join(prime_lend_rate, by='Date') %>% 
    left_join(consumer_debt_to_income, by='Date') %>% 
    left_join(comm_ind_loans_all_banks, by='Date') %>% 
    left_join(outstanding_loans, by='Date')
tail(dataAll)
```

```{r}
dataAllInterpolated <- dataAll %>% 
  mutate(HousePriceIndex = na.spline(HousePriceIndex)) %>% 
  mutate(RealGDP = na.spline(RealGDP)) %>% 
  mutate(ConsumerDebtToIncome = na.spline(ConsumerDebtToIncome))

```


```{r}
dataAllPctChange <- dataAllInterpolated %>% 
  mutate(HousePriceIndex_pct_change = (HousePriceIndex/lag(HousePriceIndex) - 1)) %>% 
  mutate(RetailTrade_pct_change = (RetailTrade/lag(RetailTrade) - 1)) %>% 
  mutate(BuildingPermits_pct_change = (BuildingPermits/lag(BuildingPermits) - 1)) %>% 
  mutate(ConsumerSentiment_pct_change = (ConsumerSentiment/lag(ConsumerSentiment) - 1)) %>% 
  mutate(AvgWeeklyHoursProd_pct_change = (AvgWeeklyHoursProd/lag(AvgWeeklyHoursProd) - 1)) %>% 
  mutate(FutureNewOrders_pct_change = (FutureNewOrders/lag(FutureNewOrders) - 1)) %>% 
  mutate(ThreemonthsIR_pct_change = (ThreemonthsIR/lag(ThreemonthsIR) - 1)) %>% 
  mutate(FiveyearsIR_pct_change = (FiveyearsIR/lag(FiveyearsIR) - 1)) %>% 
  mutate(TenyearsIR_pct_change = (TenyearsIR/lag(TenyearsIR) - 1)) %>% 
  mutate(ThirtyyearsIR_pct_change = (ThirtyyearsIR/lag(ThirtyyearsIR) - 1)) %>% 
  mutate(IndProdInd_pct_change = (IndProdInd/lag(IndProdInd) - 1)) %>% 
  mutate(DispPersIncome_pct_change = (DispPersIncome/lag(DispPersIncome) - 1)) %>% 
  mutate(ManTradeSales_pct_change = (ManTradeSales/lag(ManTradeSales) - 1)) %>% 
  mutate(InvToSales_pct_change = (InvToSales/lag(InvToSales) - 1)) %>% 
  mutate(AvgDurUnem_pct_change = (AvgDurUnem/lag(AvgDurUnem) - 1)) %>% 
  mutate(PrimeLendRate_pct_change = (PrimeLendRate/lag(PrimeLendRate) - 1)) %>% 
  mutate(CommNndLoansAllBanks_pct_change = (CommNndLoansAllBanks/lag(CommNndLoansAllBanks) - 1)) %>% 
  mutate(OutstandingLoans_pct_change = (OutstandingLoans/lag(OutstandingLoans) - 1)) %>% 
  mutate(CommNndLoansAllBanks_pct_change = (CommNndLoansAllBanks/lag(CommNndLoansAllBanks) - 1)) %>% 
  mutate(CommNndLoansAllBanks_pct_change = (CommNndLoansAllBanks/lag(CommNndLoansAllBanks) - 1)) %>% 
  mutate(RealGDP_pct_change = (RealGDP/lag(RealGDP) - 1)) %>% 
  na.omit()
```

```{r}
library(corrplot)
library(corrr)
```


```{r}
data <- dataAllPctChange %>% 
  select()

dataAllPctChange %>%
  select(HousePriceIndex_pct_change, HousePriceIndex) %>%
  correlate() %>%
  rearrange() %>%
  shave() %>%
  rplot(print_cor = TRUE)
```



```{r}
  write_csv(dataAll, "mergedData.csv")
  write_csv(dataAllPctChange, "mergedDataPctChange.csv")
```

```{r}
exportcluster <- read_csv("Desktop/masterThesis/investmentfound/exportcluster.csv")

clusterdata <- exportcluster %>% 
  select(cluster)

dataAllPctChangeCluster <- dataAllPctChange %>% 
  mutate(cluster = clusterdata)


dataAllPctChangeCluster <- cbind(dataAllPctChange, clusterdata)

dataAllPctChangeCluster %>%
  ggplot(aes(x = Date, y = TenyearsIR)) +
  geom_point(aes (color = factor (cluster)), size = 1)
 
```

