---
title: "Final Document"
output: html_document
date: "2022-12-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading required libraries
```{r}
library(Quandl)
library(forecast)
library(tidyverse)
library(ggplot2)
library(PortfolioAnalytics)
library(PerformanceAnalytics)
library(quantmod)
library(TTR)
library(tidyquant)
library(timetk)
```

# Important information
```{r, eval=FALSE}

Quandl.api_key("YE-L2_sxPkntzGfHo3vZ")
EDate <- as.Date(Sys.Date())
SDate <- as.Date(EDate-365*100)
YoY <- as.Date(EDate-365)

EFDate <- as.Date(Sys.Date())
SFDate <- EFDate - 365*100
```

## Stock market
```{r}
# S&P500 Prices
stockmarket <- tq_get("^GSPC",
                      from = SDate,
                      get = "stock.prices") %>%
  tq_transmute(select = adjusted, mutate_fun = to.monthly, indexAt = "firstof")%>% 
  rename(Date = date)

## Plotting SP500
ggplot(data = stockmarket, aes(Date, adjusted)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "S&P 500 Adjusted", labels = scales::label_dollar()) +
  ggtitle('Historical value of the S&P 500 index') +
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = 0, ymax = 5000, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = 0, ymax = 5000, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = 0, ymax = 5000, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = 0, ymax = 5000, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = 0, ymax = 5000, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = 0, ymax = 5000, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = 0, ymax = 5000, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1969/12/01"), xmax = as.Date("1970/11/01"), ymin = 0, ymax = 5000, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1960/04/01"), xmax = as.Date("1961/02/01"), ymin = 0, ymax = 5000, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1957/08/01"), xmax = as.Date("1958/04/01"), ymin = 0, ymax = 5000, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1953/07/01"), xmax = as.Date("1954/05/01"), ymin = 0, ymax = 5000, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1948/11/01"), xmax = as.Date("1949/10/01"), ymin = 0, ymax = 5000, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1945/02/01"), xmax = as.Date("1945/10/01"), ymin = 0, ymax = 5000, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1937/05/01"), xmax = as.Date("1938/06/01"), ymin = 0, ymax = 5000, alpha = .2, fill = 'purple')


# S&P500 Returns
stockmarket_returns <- stockmarket %>%
  tq_transmute(select = adjusted,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "SP500Returns")

## Plotting SP500 Returns
ggplot(data = stockmarket_returns, aes(Date, SP500Returns)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "S&P 500 monthly returns", labels = scales::percent) +
  ggtitle('Historical monthly returns of the S&P 500 index')  +
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = -0.3, ymax = 0.4, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = -0.3, ymax = 0.4, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = -0.3, ymax = 0.4, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = -0.3, ymax = 0.4, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = -0.3, ymax = 0.4, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = -0.3, ymax = 0.4, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = -0.3, ymax = 0.4, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1969/12/01"), xmax = as.Date("1970/11/01"), ymin = -0.3, ymax = 0.4, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1960/04/01"), xmax = as.Date("1961/02/01"), ymin = -0.3, ymax = 0.4, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1957/08/01"), xmax = as.Date("1958/04/01"), ymin = -0.3, ymax = 0.4, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1953/07/01"), xmax = as.Date("1954/05/01"), ymin = -0.3, ymax = 0.4, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1948/11/01"), xmax = as.Date("1949/10/01"), ymin = -0.3, ymax = 0.4, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1945/02/01"), xmax = as.Date("1945/10/01"), ymin = -0.3, ymax = 0.4, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1937/05/01"), xmax = as.Date("1938/06/01"), ymin = -0.3, ymax = 0.4, alpha = .2, fill = 'purple')

# S&P500 Dividends
SP500_Div <- Quandl('MULTPL/SP500_DIV_MONTH', 
              start_date=SDate, 
              end_date=EDate) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

# S&P500 Dividend Yield
SP500_Div_Yield <- Quandl('MULTPL/SP500_DIV_YIELD_MONTH', 
                   start_date=SDate, 
                   end_date=EDate) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

## Plotting Dividends and Dividend yields
SP500_Div %>%
  left_join(SP500_Div_Yield, by='Date')%>% 
  ggplot(aes(x = Date, y = Value.x)) +
  geom_line(color = 'black') + 
  geom_line(aes(y = Value.y*5), color = 'dodgerblue1') + 
  scale_y_continuous('Dividends',labels = scales::label_dollar(), sec.axis = sec_axis(~./500, name="Dividend Yield", labels = scales::percent)) +
  scale_x_date(name = 'Dates') +
  theme(axis.title.y.left=element_text(color="black"),
        axis.text.y.left=element_text(color="black"), 
        axis.title.y.right=element_text(color="dodgerblue1"),
        axis.text.y.right=element_text(color="dodgerblue1")) +
  ggtitle('Historical Dividends and Dividend Yield of the S&P 500 index')+
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = 0, ymax = 70, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = 0, ymax = 70, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = 0, ymax = 70, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = 0, ymax = 70, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = 0, ymax = 70, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = 0, ymax = 70, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = 0, ymax = 70, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1969/12/01"), xmax = as.Date("1970/11/01"), ymin = 0, ymax = 70, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1960/04/01"), xmax = as.Date("1961/02/01"), ymin = 0, ymax = 70, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1957/08/01"), xmax = as.Date("1958/04/01"), ymin = 0, ymax = 70, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1953/07/01"), xmax = as.Date("1954/05/01"), ymin = 0, ymax = 70, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1948/11/01"), xmax = as.Date("1949/10/01"), ymin = 0, ymax = 70, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1945/02/01"), xmax = as.Date("1945/10/01"), ymin = 0, ymax = 70, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1937/05/01"), xmax = as.Date("1938/06/01"), ymin = 0, ymax = 70, alpha = .2, fill = 'purple')

# S&P500 PE Ratios
SP500_PE <- Quandl('MULTPL/SP500_PE_RATIO_MONTH', 
             start_date=SDate, 
             end_date=EDate) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

# S&P500 Earnings
SP500_Earnings <- Quandl('MULTPL/SP500_EARNINGS_MONTH', 
                        start_date=SDate, 
                        end_date=EDate) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

## Plotting Earnings and PE ratios
SP500_Earnings %>%
  left_join(SP500_PE, by='Date')%>% 
  ggplot(aes(x = Date, y = Value.x)) +
  geom_line(color = 'black') + 
  geom_line(aes(y = (Value.y)*1.5), color = 'dodgerblue1') + 
  scale_y_continuous('Earnings', sec.axis = sec_axis(~./1.5, name="PE Ratio")) +
  scale_x_date(name = 'Dates') +
  theme(axis.title.y.left=element_text(color="black"),
        axis.text.y.left=element_text(color="black"), 
        axis.title.y.right=element_text(color="dodgerblue1"),
        axis.text.y.right=element_text(color="dodgerblue1")) +
  ggtitle('Historical Earnings and PE ratios of the S&P 500 index')+
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = 0, ymax = 220, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = 0, ymax = 220, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = 0, ymax = 220, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = 0, ymax = 220, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = 0, ymax = 220, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = 0, ymax = 220, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = 0, ymax = 220, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1969/12/01"), xmax = as.Date("1970/11/01"), ymin = 0, ymax = 220, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1960/04/01"), xmax = as.Date("1961/02/01"), ymin = 0, ymax = 220, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1957/08/01"), xmax = as.Date("1958/04/01"), ymin = 0, ymax = 220, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1953/07/01"), xmax = as.Date("1954/05/01"), ymin = 0, ymax = 220, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1948/11/01"), xmax = as.Date("1949/10/01"), ymin = 0, ymax = 220, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1945/02/01"), xmax = as.Date("1945/10/01"), ymin = 0, ymax = 220, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1937/05/01"), xmax = as.Date("1938/06/01"), ymin = 0, ymax = 220, alpha = .2, fill = 'purple')


## Plotting Earnings and Payout ratios of the S&P 500 Index
SP500_Earnings %>%
  left_join(SP500_Div, by='Date')%>% 
  ggplot(aes(x = Date, y = Value.x)) +
  geom_line(color = 'black') + 
  geom_line(aes(y = (Value.y/Value.x)*80), color = 'dodgerblue1') + 
  scale_y_continuous('Earnings', labels = scales::label_dollar(), sec.axis = sec_axis(~./800, name="Payout Ratio", labels = scales::percent)) +
  scale_x_date(name = 'Dates') +
  theme(axis.title.y.left=element_text(color="black"),
        axis.text.y.left=element_text(color="black"), 
        axis.title.y.right=element_text(color="dodgerblue1"),
        axis.text.y.right=element_text(color="dodgerblue1")) +
  ggtitle('Historical Earnings and Payout ratio of the S&P 500 index')+
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = 0, ymax = 320, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = 0, ymax = 320, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = 0, ymax = 320, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = 0, ymax = 320, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = 0, ymax = 320, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = 0, ymax = 320, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = 0, ymax = 320, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1969/12/01"), xmax = as.Date("1970/11/01"), ymin = 0, ymax = 320, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1960/04/01"), xmax = as.Date("1961/02/01"), ymin = 0, ymax = 320, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1957/08/01"), xmax = as.Date("1958/04/01"), ymin = 0, ymax = 320, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1953/07/01"), xmax = as.Date("1954/05/01"), ymin = 0, ymax = 320, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1948/11/01"), xmax = as.Date("1949/10/01"), ymin = 0, ymax = 320, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1945/02/01"), xmax = as.Date("1945/10/01"), ymin = 0, ymax = 320, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1937/05/01"), xmax = as.Date("1938/06/01"), ymin = 0, ymax = 320, alpha = .2, fill = 'purple')

```

## All-Transactions House Price Index for the United States
```{r}

# FRED All-Transactions House Price Index for the United States 
house_price_index <- tq_get("USSTHPI",
                            from = SDate,
                            "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(HousePriceIndex = price)%>% 
  rename(Date = date)

house_price_index %>% 
  ggplot(aes(Date, HousePriceIndex)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "House price index") +
  ggtitle('FRED All-transactions House price index (Index Jan 1980 = 100)')+
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = 0, ymax = 650, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = 0, ymax = 650, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = 0, ymax = 650, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = 0, ymax = 650, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = 0, ymax = 650, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = 0, ymax = 650, alpha = .2, fill = 'purple')
```

## FRED Total Retail Trade
```{r}

# FRED All Employees, Retail Trade
retail_trade <- tq_get("USASARTMISMEI", 
                            from =SDate, 
                            get = "economic.data")%>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(RetailTrade = price) %>% 
  rename(Date = date)

retail_trade %>% 
  ggplot(aes(Date, RetailTrade)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "Total retail trade") +
  ggtitle('FRED Total retail trade index (Index Jan 2015 = 100)')+
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = 0, ymax = 150, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = 0, ymax = 150, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = 0, ymax = 150, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = 0, ymax = 150, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = 0, ymax = 150, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = 0, ymax = 150, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = 0, ymax = 150, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1969/12/01"), xmax = as.Date("1970/11/01"), ymin = 0, ymax = 150, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1960/04/01"), xmax = as.Date("1961/02/01"), ymin = 0, ymax = 150, alpha = .2, fill = 'purple')
```


## Interest rates
```{r}

# T-Bills
threemonths_IR <- tq_get("DTB3",
                         from = SDate,
                         "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(ThreemonthsIR = price) %>% 
  rename(Date = date)

# Five-y Bonds
fiveyears_IR <-  tq_get("DGS5",
                         from = SDate,
                         "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(FiveyearsIR = price) %>% 
  rename(Date = date)

# Ten-y Bonds
tenyears_IR <-  tq_get("DGS10",
                         from = SDate,
                         "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(TenyearsIR = price) %>% 
  rename(Date = date)
  
# Thirty-y Bonds
thirtyyears_IR <- tq_get("DGS30",
                         from = SDate,
                         "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(ThirtyyearsIR = price) %>% 
  rename(Date = date)

# Dataframe with rates
rates <- threemonths_IR %>%
  left_join(fiveyears_IR, by='Date')%>% 
  left_join(tenyears_IR, by='Date')%>% 
  left_join(thirtyyears_IR, by='Date') %>% 
  na.omit()

# Plotting interest rates
rates %>% 
  ggplot(aes(x = Date)) +
  geom_line(aes(y = ThreemonthsIR/100, color = "3 months")) + 
  geom_line(aes(y = FiveyearsIR/100, color = "5 years")) +
  geom_line(aes(y = TenyearsIR/100, color = "10 years")) +
  geom_line(aes(y = ThirtyyearsIR/100, color = "30 years")) +
  scale_y_continuous('Interest rates', labels = scales::percent) +
  scale_x_date(name = 'Dates') +
  scale_color_manual(name = "Interest rate", values = c( "10 years" = "red", "3 months" = "black","30 years" = "green",  "5 years" = "dodgerblue" ), labels = c("10 years", "3 months", "30 years", "5 years")) +
  ggtitle('Historical Interest rates for US bonds')+
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = 0, ymax = 0.17, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = 0, ymax = 0.17, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = 0, ymax = 0.17, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = 0, ymax = 0.17, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = 0, ymax = 0.17, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = 0, ymax = 0.17, alpha = .2, fill = 'purple')

# 30y - 3m spread

IR_Spread <- thirtyyears_IR %>%
    left_join(threemonths_IR, by='Date') %>% 
  mutate(IRSpread = ThirtyyearsIR - ThreemonthsIR) %>% 
  select(-ThirtyyearsIR, -ThreemonthsIR)

# Plotting spreads

IR_Spread %>% 
  ggplot(aes(Date, IRSpread/100)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "Interest spread", labels = scales::percent) +
  ggtitle('Interest rate spread (3y - 3m)')+
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = -0.025, ymax = 0.05, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = -0.025, ymax = 0.05, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = -0.025, ymax = 0.05, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = -0.025, ymax = 0.05, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = -0.025, ymax = 0.05, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = -0.025, ymax = 0.05, alpha = .2, fill = 'purple')
```

## Building permits
```{r}

# FRED Building Permits
building_permits <-  tq_get("PERMIT",
                         from = SDate,
                         "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(BuildingPermits = price) %>% 
  rename(Date = date)

building_permits %>% 
  ggplot(aes(Date, BuildingPermits)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "N° of building permits") +
  ggtitle('Historical development of building permits')+
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = 500, ymax = 2500, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = 500, ymax = 2500, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = 500, ymax = 2500, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = 500, ymax = 2500, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = 500, ymax = 2500, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = 500, ymax = 2500, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = 500, ymax = 2500, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1969/12/01"), xmax = as.Date("1970/11/01"), ymin = 500, ymax = 2500, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1960/04/01"), xmax = as.Date("1961/02/01"), ymin = 500, ymax = 2500, alpha = .2, fill = 'purple')

```

## Consumer sentiment
```{r}

# Index of consumer sentiment
consumer_sentiment <- Quandl("UMICH/SOC1",start_date=SDate, end_date=EDate, collapse = "monthly") %>% 
  rename(ConsumerSentiment = Index) %>% 
  mutate(Date = floor_date(Date, unit = "month"))

consumer_sentiment %>% 
  ggplot(aes(Date, ConsumerSentiment)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "Index of consumer sentiment") +
  ggtitle('Historical consumer sentiment')+
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = 50, ymax = 115, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = 50, ymax = 115, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = 50, ymax = 115, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = 50, ymax = 115, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = 50, ymax = 115, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = 50, ymax = 115, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = 50, ymax = 115, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1969/12/01"), xmax = as.Date("1970/11/01"), ymin = 50, ymax = 115, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1960/04/01"), xmax = as.Date("1961/02/01"), ymin = 50, ymax = 115, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1957/08/01"), xmax = as.Date("1958/04/01"), ymin = 50, ymax = 115, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1953/07/01"), xmax = as.Date("1954/05/01"), ymin = 50, ymax = 115, alpha = .2, fill = 'purple')
```

## Average Weekly Hours of Production and Nonsupervisory Employees, Manufacturing
```{r}

# FRED average weekly hours of Production and Nonsupervisory Employees, Manufacturing
avg_weekly_hours_prod <- tq_get("AWHMAN", 
                            from =SDate, 
                            get = "economic.data") %>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(AvgWeeklyHoursProd = price) %>% 
  rename(Date = date)

avg_weekly_hours_prod %>% 
  ggplot(aes(Date, AvgWeeklyHoursProd)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "Weekly hours of manufacturing") +
  ggtitle('Average Weekly Hours of Production and Nonsupervisory Employees, Manufacturing')+
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = 37, ymax = 46, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = 37, ymax = 46, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = 37, ymax = 46, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = 37, ymax = 46, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = 37, ymax = 46, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = 37, ymax = 46, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = 37, ymax = 46, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1969/12/01"), xmax = as.Date("1970/11/01"), ymin = 37, ymax = 46, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1960/04/01"), xmax = as.Date("1961/02/01"), ymin = 37, ymax = 46, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1957/08/01"), xmax = as.Date("1958/04/01"), ymin = 37, ymax = 46, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1953/07/01"), xmax = as.Date("1954/05/01"), ymin = 37, ymax = 46, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1948/11/01"), xmax = as.Date("1949/10/01"), ymin = 37, ymax = 46, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1945/02/01"), xmax = as.Date("1945/10/01"), ymin = 37, ymax = 46, alpha = .2, fill = 'purple')

```
## Future New Orders; Diffusion Index for Federal Reserve District 3: Philadelphia
```{r}

# FRED Future New Orders; Diffusion Index for Federal Reserve District 3: Philadelphia
future_new_orders <- tq_get("NOFDFSA066MSFRBPHI", 
                            from =SDate, 
                            get = "economic.data")%>% 
  tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% 
  rename(FutureNewOrders = price) %>% 
  rename(Date = date)

future_new_orders %>% 
  ggplot(aes(Date, FutureNewOrders)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "Future new orders") +
  ggtitle('Future New Orders; Diffusion Index for Federal Reserve District 3: Philadelphia')+
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = -50, ymax = 90, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = -50, ymax = 90, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = -50, ymax = 90, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = -50, ymax = 90, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = -50, ymax = 90, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = -50, ymax = 90, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = -50, ymax = 90, alpha = .2, fill = 'purple')
```

# Indexation of leading indicators
```{r}
#library(stats)

pca_data <- stockmarket_returns %>% 
  left_join(retail_trade, by = "Date") %>% 
  left_join(IR_Spread, by = "Date") %>%
  left_join(building_permits, by = "Date") %>%
  left_join(consumer_sentiment, by = "Date") %>%
  left_join(avg_weekly_hours_prod, by = "Date") %>%
  left_join(future_new_orders, by = "Date") %>% 
  select(-Date) %>% 
  na.omit()

pca_result <- princomp(pca_data)
pca_result$scores
pca_result$sdev

pca_summary <- summary(pca_result)
pca_variances <- var(pca_result$scores)
pca_cumulative_variances <- cumsum(pca_variances)

pca_var <- pca_result$sdev^2 / sum(pca_result$sdev^2)
barplot(pca_var, xlab="Principal Component", ylab="Proportion of Variance Explained")

screeplot(pca_result, type="line", main="Scree Plot")

plot(pca_result$scores[,1:2], col=1:nrow(pca_result$scores), xlab="PC1", ylab="PC2")

pca_scores <- as.data.frame(pca_result$scores) %>% 
  select(Comp.1)

values <- stockmarket_returns %>% 
  left_join(retail_trade, by = "Date") %>% 
  left_join(IR_Spread, by = "Date") %>%
  left_join(building_permits, by = "Date") %>%
  left_join(consumer_sentiment, by = "Date") %>%
  left_join(avg_weekly_hours_prod, by = "Date") %>%
  left_join(future_new_orders, by = "Date") %>%
  na.omit()

values$index <- pca_scores[,1]

plot(values$Date, values$index)

values %>% 
  ggplot(aes(Date, index)) + 
  geom_line() +
  scale_x_date(name = "Year", date_minor_breaks = "10 year") + 
  scale_y_continuous(name = "Leading index") +
  ggtitle('Leading index for business cycle') +
  annotate("rect", xmin = as.Date("2020/02/01"), xmax = as.Date("2020/04/01"), ymin = -1000, ymax = 1000, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2007/12/01"), xmax = as.Date("2009/06/01"), ymin = -1000, ymax = 1000, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("2001/03/01"), xmax = as.Date("2001/11/01"), ymin = -1000, ymax = 1000, alpha = .2, fill = 'purple') +
  annotate("rect", xmin = as.Date("1990/07/01"), xmax = as.Date("1991/03/01"), ymin = -1000, ymax = 1000, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1981/07/01"), xmax = as.Date("1982/11/01"), ymin = -1000, ymax = 1000, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1980/01/01"), xmax = as.Date("1980/07/01"), ymin = -1000, ymax = 1000, alpha = .2, fill = 'purple')+
  annotate("rect", xmin = as.Date("1973/11/01"), xmax = as.Date("1975/05/01"), ymin = -1000, ymax = 1000, alpha = .2, fill = 'purple')
  

```

