---
title: "Investment Fund"
output: html_document
date: "2022-10-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#libraries
library(xts)
library(PerformanceAnalytics)
library(quantmod)
library(pastecs)
library(psych)
library(Quandl)
library("fredr")
library(Quandl)
library(PerformanceAnalytics)
library(ggplot2)
library(forecast)
library(tidyverse)
library("timetk")
library("tidyquant")
```

```{r}
Quandl.api_key("4nDDuxoarbX1eR9z7KY-") # I don't think we all can use the same api_key, therefore make an account with quandl, it's for free.
```

```{r}
EDate <- Sys.Date()
SDate <- EDate-365*80

YoY <- as.Date(EDate-365)

```

```{r}
#GDP from tq get is missing some data
#GDP <- tq_get("GDP", get = "economic.data", start_date=SDate, end_date=EDate, collapse = "quarterly") %>% 
 # tq_transmute(select = price, mutate_fun = to.monthly, indexAt = "firstof") %>% tq_transmute(select = price,         
  #             mutate_fun = periodReturn,   
   #            period = "quarterly",      
    #           col_rename = "price") %>% rename(GDPGROWTH = price) %>% 
  #rename(Date = date)
########################################################
#GDP
GDP <- Quandl('FRED/GDP', start_date=SDate, end_date=EDate, collapse = "quarterly") %>% 
  tq_transmute(select = Value, mutate_fun = to.monthly, indexAt = "firstof") %>% tq_transmute(select = Value,         
               mutate_fun = periodReturn,   
               period = "quarterly",      
               col_rename = "Value") 
########################################################

potentialGDP <-Quandl('FRED/NGDPPOT', start_date=SDate, end_date=EDate, collapse = "quarterly") %>% 
  tq_transmute(select = Value, mutate_fun = to.monthly, indexAt = "firstof") %>% tq_transmute(select = Value,         
               mutate_fun = periodReturn,   
               period = "quarterly",      
               col_rename = "Value") 



dates <-Quandl('FRED/JHDUSRGDPBR', start_date=SDate, end_date=EDate, collapse = "quarterly") %>% 
  tq_transmute(select = Value, mutate_fun = to.monthly, indexAt = "firstof")


ddd <- GDP %>% 
  left_join(dates, by = "Date") %>%
  left_join(potentialGDP, by = "Date") %>%
  na.omit()

ddd$dif <- (ddd$Value.x - ddd$Value)/ddd$Value

difdensity <- density(ddd$dif)
plot(difdensity)

Recession <- subset(ddd, Value.y == 1 , select=c(Date, Value.x, Value.y, dif))
expansion <- subset(ddd, Value.y == 0 , select=c(Date, Value.x, Value.y, dif))
expansion$adjy <- expansion$Value.y + 1

Recessionsum <- sum(Recession$Value.y)
expansionsum <- sum(expansion$adjy)
FrequencyOfRecession <- Recessionsum/(Recessionsum+expansionsum)

RecessionDensity <- (density(Recession$dif)) 

#RecessionDensity1 <- (density(Recession$dif)) 
#RecessionDensity1$x <-  RecessionDensity$x * FrequencyOfRecession

ExpanssionDensity <- density(expansion$dif)
GDPdensity <- density(GDP$Value)

plot(RecessionDensity)
plot(ExpanssionDensity)
plot(GDPdensity)
