---
title: "Sectors"
output: html_document
date: "2022-12-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(Quandl)
library(forecast)
library(tidyverse)
library(ggplot2)
library(rlang)
library(PortfolioAnalytics)
library(PerformanceAnalytics)
library(pROC)
library(quantmod)
library(TTR)
library(tidyquant)
library(timetk)
```

#Important tickers are the following:
S&P Communication Services Select Sector (XLC) -> DONE
S&P Consumer Discretionary Select Sector (XLY)
S&P Consumer Staples Select Sector (XLP)
S&P Energy Select Sector (XLE) -> DONE
S&P Financial Select Sector (XLF)
S&P Health Care Select Sector (XLV)
S&P Industrial Select Sector (XLI)
S&P Materials Select Sector (XLB) -> DONE
S&P Real Estate Select Sector (XLRE) -> DONE
S&P Technology Select Sector (XLK) -> DONE
S&P Utilities Select Sector (XLU) -> DONE

```{r}
# SP500 - ^GSPC

SP500 <- tq_get("^GSPC",
                      from ="1920-01-01",
                      get = "stock.prices")%>% 
  tq_transmute(select = adjusted, mutate_fun = to.monthly, indexAt = "firstof", col_rename = "SP500")%>% 
  rename(Date = date)

SP500_returns <- SP500 %>%
  tq_transmute(select = SP500,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "SP500_returns")

plot(y= SP500$SP500, x= SP500$Date )

SP500_returns %>%
  ggplot(aes(x = Date, y = SP500_returns)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Monthly returns") +
  ggtitle("Monthly Returns for SP500") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 

SP500_returns %>%
  ggplot(aes(x = SP500_returns)) +
  geom_histogram(binwidth = 0.015) +
  theme_classic() +
  labs(x = "Monthly returns") +
  ggtitle("Monthly Returns for SP500") +
  scale_x_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) +
  annotate(geom = 'text', x = -0.30, y = 8, label = "Extremely\nnegative\nreturns") +
  annotate(geom = 'text', x = 0.430, y = 8, label = "Extremely\npositive\nreturns")

```


```{r}
#Communication sector - XLC

communication <- tq_get("XLC",
                      from ="1920-01-01",
                      get = "stock.prices")%>% 
  tq_transmute(select = adjusted, mutate_fun = to.monthly, indexAt = "firstof", col_rename = "XLC")%>% 
  rename(Date = date)

communication_returns <- communication %>%
  tq_transmute(select = XLC,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "XLC_returns")

plot(y= communication$XLC, x= communication$Date )

communication_returns %>%
  ggplot(aes(x = Date, y = XLC_returns)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Monthly returns") +
  ggtitle("Monthly Returns for XLC") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 

communication_returns %>%
  ggplot(aes(x = XLC_returns)) +
  geom_histogram(binwidth = 0.015) +
  theme_classic() +
  labs(x = "Monthly returns") +
  ggtitle("Monthly Returns for XLC") +
  scale_x_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) +
  annotate(geom = 'text', x = -0.30, y = 8, label = "Extremely\nnegative\nreturns") +
  annotate(geom = 'text', x = 0.430, y = 8, label = "Extremely\npositive\nreturns")

```

```{r}
# Consumer Discretionary Sector - XLY

cons_discr <- tq_get("XLY",
                      from ="1920-01-01",
                      get = "stock.prices")%>% 
  tq_transmute(select = adjusted, mutate_fun = to.monthly, indexAt = "firstof", col_rename = "XLY")%>% 
  rename(Date = date)

cons_discr_returns <- cons_discr %>%
  tq_transmute(select = XLY,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "XLY_returns")

plot(y= cons_discr$XLY, x= cons_discr$Date )

cons_discr_returns %>%
  ggplot(aes(x = Date, y = XLY_returns)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Monthly returns") +
  ggtitle("Monthly Returns for XLY") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 

cons_discr_returns %>%
  ggplot(aes(x = XLY_returns)) +
  geom_histogram(binwidth = 0.015) +
  theme_classic() +
  labs(x = "Monthly returns") +
  ggtitle("Monthly Returns for XLY") +
  scale_x_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) +
  annotate(geom = 'text', x = -0.30, y= 40, label = "Extremely\nnegative\nreturns") +
  annotate(geom = 'text', x = 0.430, y = 40, label = "Extremely\npositive\nreturns")
```

```{r}
# Consumer Staples sector - XLP

cons_stapl <- tq_get("XLP",
                      from ="1920-01-01",
                      get = "stock.prices")%>% 
  tq_transmute(select = adjusted, mutate_fun = to.monthly, indexAt = "firstof", col_rename = "XLP")%>% 
  rename(Date = date)

cons_stapl_returns <- cons_stapl %>%
  tq_transmute(select = XLP,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "XLP_returns")

plot(y= cons_stapl$XLP, x= cons_stapl$Date )

cons_stapl_returns %>%
  ggplot(aes(x = Date, y = XLP_returns)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Monthly returns") +
  ggtitle("Monthly Returns for XLE") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 

cons_stapl_returns %>%
  ggplot(aes(x = XLP_returns)) +
  geom_histogram(binwidth = 0.015) +
  theme_classic() +
  labs(x = "Monthly returns") +
  ggtitle("Monthly Returns for XLP") +
  scale_x_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) +
  annotate(geom = 'text', x = -0.30, y= 40, label = "Extremely\nnegative\nreturns") +
  annotate(geom = 'text', x = 0.430, y = 40, label = "Extremely\npositive\nreturns")
```

```{r}
#Energy sector - XLE

energy <- tq_get("XLE",
                      from ="1920-01-01",
                      get = "stock.prices")%>% 
  tq_transmute(select = adjusted, mutate_fun = to.monthly, indexAt = "firstof", col_rename = "XLE")%>% 
  rename(Date = date)

energy_returns <- energy %>%
  tq_transmute(select = XLE,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "XLE_returns")

plot(y= energy$XLE, x= energy$Date )

energy_returns %>%
  ggplot(aes(x = Date, y = XLE_returns)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Monthly returns") +
  ggtitle("Monthly Returns for XLE") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 

energy_returns %>%
  ggplot(aes(x = XLE_returns)) +
  geom_histogram(binwidth = 0.015) +
  theme_classic() +
  labs(x = "Monthly returns") +
  ggtitle("Monthly Returns for XLE") +
  scale_x_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) +
  annotate(geom = 'text', x = -0.30, y= 30, label = "Extremely\nnegative\nreturns") +
  annotate(geom = 'text', x = 0.430, y = 30, label = "Extremely\npositive\nreturns")
```

```{r}
# Financial sector - XLF

finance <- tq_get("XLF",
                      from ="1920-01-01",
                      get = "stock.prices")%>% 
  tq_transmute(select = adjusted, mutate_fun = to.monthly, indexAt = "firstof", col_rename = "XLF")%>% 
  rename(Date = date)

finance_returns <- finance %>%
  tq_transmute(select = XLF,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "XLF_returns")

plot(y= finance$XLF, x= finance$Date )

finance_returns %>%
  ggplot(aes(x = Date, y = XLF_returns)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Monthly returns") +
  ggtitle("Monthly Returns for XLF") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 

finance_returns %>%
  ggplot(aes(x = XLF_returns)) +
  geom_histogram(binwidth = 0.015) +
  theme_classic() +
  labs(x = "Monthly returns") +
  ggtitle("Monthly Returns for XLF") +
  scale_x_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) +
  annotate(geom = 'text', x = -0.30, y= 30, label = "Extremely\nnegative\nreturns") +
  annotate(geom = 'text', x = 0.430, y = 30, label = "Extremely\npositive\nreturns")

```

```{r}
# Healthcare sector - XLV

healthcare <- tq_get("XLV",
                      from ="1920-01-01",
                      get = "stock.prices")%>% 
  tq_transmute(select = adjusted, mutate_fun = to.monthly, indexAt = "firstof", col_rename = "XLV")%>% 
  rename(Date = date)

healthcare_returns <- healthcare %>%
  tq_transmute(select = XLV,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "XLV_returns")

plot(y= healthcare$XLV, x= healthcare$Date )

healthcare_returns %>%
  ggplot(aes(x = Date, y = XLV_returns)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Monthly returns") +
  ggtitle("Monthly Returns for XLV") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 

healthcare_returns %>%
  ggplot(aes(x = XLV_returns)) +
  geom_histogram(binwidth = 0.015) +
  theme_classic() +
  labs(x = "Monthly returns") +
  ggtitle("Monthly Returns for XLV") +
  scale_x_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) +
  annotate(geom = 'text', x = -0.30, y= 40, label = "Extremely\nnegative\nreturns") +
  annotate(geom = 'text', x = 0.430, y = 40, label = "Extremely\npositive\nreturns")

```

```{r}
# Industrial sector - XLI

industrial <- tq_get("XLI",
                      from ="1920-01-01",
                      get = "stock.prices")%>% 
  tq_transmute(select = adjusted, mutate_fun = to.monthly, indexAt = "firstof", col_rename = "XLI")%>% 
  rename(Date = date)

industrial_returns <- industrial %>%
  tq_transmute(select = XLI,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "XLI_returns")

plot(y= industrial$XLI, x= industrial$Date )

industrial_returns %>%
  ggplot(aes(x = Date, y = XLI_returns)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Monthly returns") +
  ggtitle("Monthly Returns for XLI") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 

industrial_returns %>%
  ggplot(aes(x = XLI_returns)) +
  geom_histogram(binwidth = 0.015) +
  theme_classic() +
  labs(x = "Monthly returns") +
  ggtitle("Monthly Returns for XLI") +
  scale_x_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) +
  annotate(geom = 'text', x = -0.30, y= 40, label = "Extremely\nnegative\nreturns") +
  annotate(geom = 'text', x = 0.430, y = 40, label = "Extremely\npositive\nreturns")

```

```{r}
#Materials sector - XLB

materials <- tq_get("XLB",
                      from ="1920-01-01",
                      get = "stock.prices")%>% 
  tq_transmute(select = adjusted, mutate_fun = to.monthly, indexAt = "firstof", col_rename = "XLB")%>% 
  rename(Date = date)

materials_returns <- materials %>%
  tq_transmute(select = XLB,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "XLB_returns")

plot(y= materials$XLB, x= materials$Date )

materials_returns %>%
  ggplot(aes(x = Date, y = XLB_returns)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Monthly returns") +
  ggtitle("Monthly Returns for XLB") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 

materials_returns %>%
  ggplot(aes(x = XLB_returns)) +
  geom_histogram(binwidth = 0.015) +
  theme_classic() +
  labs(x = "Monthly returns") +
  ggtitle("Monthly Returns for XLB") +
  scale_x_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) +
  annotate(geom = 'text', x = -0.30, y= 30, label = "Extremely\nnegative\nreturns") +
  annotate(geom = 'text', x = 0.430, y = 30, label = "Extremely\npositive\nreturns")

```

```{r}
#Real Estate sector - XLRE

real_estate <- tq_get("XLRE",
                      from ="1920-01-01",
                      get = "stock.prices")%>% 
  tq_transmute(select = adjusted, mutate_fun = to.monthly, indexAt = "firstof", col_rename = "XLRE")%>% 
  rename(Date = date)

real_estate_returns <- real_estate %>%
  tq_transmute(select = XLRE,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "XLRE_returns")

plot(y= real_estate$XLRE, x= real_estate$Date )

real_estate_returns %>%
  ggplot(aes(x = Date, y = XLRE_returns)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Monthly returns") +
  ggtitle("Monthly Returns for XLRE") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 

real_estate_returns %>%
  ggplot(aes(x = XLRE_returns)) +
  geom_histogram(binwidth = 0.015) +
  theme_classic() +
  labs(x = "Monthly returns") +
  ggtitle("Monthly Returns for XLRE") +
  scale_x_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) +
  annotate(geom = 'text', x = -0.30, y= 15, label = "Extremely\nnegative\nreturns") +
  annotate(geom = 'text', x = 0.430, y = 15, label = "Extremely\npositive\nreturns")
```

```{r}
#Technology sector - XLK

technology <- tq_get("XLK",
                      from ="1920-01-01",
                      get = "stock.prices")%>% 
  tq_transmute(select = adjusted, mutate_fun = to.monthly, indexAt = "firstof", col_rename = "XLK")%>% 
  rename(Date = date)

technology_returns <- technology %>%
  tq_transmute(select = XLK,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "XLK_returns")

plot(y= technology$XLK, x= technology$Date )

technology_returns %>%
  ggplot(aes(x = Date, y = XLK_returns)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Monthly returns") +
  ggtitle("Monthly Returns for XLK") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 

technology_returns %>%
  ggplot(aes(x = XLK_returns)) +
  geom_histogram(binwidth = 0.015) +
  theme_classic() +
  labs(x = "Monthly returns") +
  ggtitle("Monthly Returns for XLk") +
  scale_x_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) +
  annotate(geom = 'text', x = -0.30, y= 30, label = "Extremely\nnegative\nreturns") +
  annotate(geom = 'text', x = 0.430, y = 30, label = "Extremely\npositive\nreturns")

```

```{r}
#Utilities sector - XLU

utilities <- tq_get("XLU",
                      from ="1920-01-01",
                      get = "stock.prices")%>% 
  tq_transmute(select = adjusted, mutate_fun = to.monthly, indexAt = "firstof", col_rename = "XLU")%>% 
  rename(Date = date)

utilities_returns <- utilities %>%
  tq_transmute(select = XLU,         
               mutate_fun = periodReturn,   
               period = "monthly",      
               col_rename = "XLU_returns")

plot(y= utilities$XLU, x= utilities$Date )

utilities_returns %>%
  ggplot(aes(x = Date, y = XLU_returns)) +
  geom_line() +
  theme_classic() +
  labs(x = "Date", y = "Monthly returns") +
  ggtitle("Monthly Returns for XLU") +
  scale_x_date(date_breaks = "years", date_labels = "%Y") +
  scale_y_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) 

utilities_returns %>%
  ggplot(aes(x = XLU_returns)) +
  geom_histogram(binwidth = 0.015) +
  theme_classic() +
  labs(x = "Monthly returns") +
  ggtitle("Monthly Returns for XLU") +
  scale_x_continuous(breaks = seq(-0.5,0.6,0.05),
                     labels = scales::percent) +
  annotate(geom = 'text', x = -0.30, y= 40, label = "Extremely\nnegative\nreturns") +
  annotate(geom = 'text', x = 0.430, y = 40, label = "Extremely\npositive\nreturns")
```
# Data frame with all
```{r}

allsectors <- SP500 %>%
  left_join(communication, by = "Date") %>% 
  left_join(cons_discr, by = "Date") %>% 
  left_join(cons_stapl, by = "Date") %>% 
  left_join(energy, by = "Date") %>% 
  left_join(finance, by = "Date") %>% 
  left_join(healthcare, by = "Date") %>% 
  left_join(industrial, by = "Date") %>% 
  left_join(materials, by = "Date") %>% 
  left_join(real_estate, by = "Date") %>% 
  left_join(technology, by = "Date") %>% 
  left_join(utilities, by = "Date") %>% 
  na.omit()

```










